### 2021-03-12 README.Rmd
add

---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "80%",
  fig.align = "center"
)
```

# Steve's Academic R Projects

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

```{r, echo = FALSE, results='asis'}
cat(
	badge_cran_release("steveproj", "green"),
	badge_cran_download("steveproj", "grand-total", "green"),
	badge_cran_download("steveproj", "last-month", "green"),
	badge_cran_download("steveproj", "last-week", "green")
)
```

<img src="http://svmiller.com/images/steveproj-hexlogo.png" alt="My steveproj hexlogo" align="right" width="200" style="padding: 0 15px; float: right;"/>

`{steveproj}` is an R package to help you start and manage R projects with an eye toward producing an academic project (to culminate in an academic paper). The package is in development and will incorporate other packages in my eponymous R ecosystem, prominently [`{stevetemplates}`](https://github.com/svmiller/stevetemplates). The package itself leans primarily on Rstudio and how it creates/manages projects. The creation a project in Rstudio, through `{steveproj}`, will result in a new directory containing subdirectories for rendering documents (`src`), R scripts for analysis (`R`), finished data objects (`data`), and finished reports (`doc`). An accompanying `Makefile` and R Markdown file will assist in the management and production of the project.

## Installation

When the time comes, you can install this on CRAN.

```r
install.packages("steveproj")
```

Right now, this package in development and is not available on CRAN. You can install the development version of `steveproj` from Github via the `devtools` package. I suppose using the `remotes` package would work as well.

```r
devtools::install_github("svmiller/steveproj")
```

## Usage

My website will have a more exhaustive tutorial for using this package and all that comes in it. For now, a user maximize their experience with `{steveproj}` through either the console or Rstudio.

### Console

Assume the current working directory is something like `/home/steve/Dropbox/projects` (as it is for me). Then, a user can create a new project with the `create_project()` command.

```{r, eval=F}
steveproj::create_project("dissertation")
```

This will create a new directory in the working directory, titled "dissertation", that includes a skeleton of a research project to assist the user in getting started on their academic paper/project. The only downside to the console approach over the Rstudio approach is the console approach won't create an `.Rproj` file in the directory. The Rstudio approach will.

### Rstudio

Go to *File > New Project*. You'll see a prompt that looks like this. Select "New Directory".

![](inst/README/steveproj-1.png)

That will direct you here. Scroll down your available project types until you see my "Steve project" entry. It will have that "S" icon (that is incidentally the icon for my website). Select it.

![](inst/README/steveproj-2.png)

That will direct you here. Enter the name of the directory you want to create. Click "Create Project" when you're done. This will create a new directory, titled whatever you entered in the directory name, along with an `.Rproj` file. By default, it will also open a new Rstudio session.

![](inst/README/steveproj-3.png)

### 2021-03-13 README.Rmd
new function

@@
 This will create a new directory in the working directory, titled "dissertation", that includes a skeleton of a research project to assist the user in getting started on their academic paper/project.
+That directory will be located in the current working directory.
 The only downside to the console approach over the Rstudio approach is the console approach won't create an `.Rproj` file in the directory.
 The Rstudio approach will.
+
+You could optionally combine this command line call in the console with the following command, which will add an `.Rproj` file to the directory you just created
+
+```{r, eval=F}
+# steveproj::create_project("dissertation")
+# ^ assume you just ran this
+# Then, do this next
+steveproj::create_rproj("dissertation")
+```
 

### 2021-03-13 README.Rmd
addy mcaddadd

@@
 
-That will direct you here. Scroll down your available project types until you see my "Steve project" entry. It will have that "S" icon (that is incidentally the icon for my website). Select it.
+That will direct you here.
+Scroll down your available project types until you see my "S" icon, which is incidentally the favicon on [my website](http://svmiller.com).
+Select that entry to create a new academic paper/project.
 

### 2021-03-15 inst/rstudio/templates/project/resources/ms.Rmd
pilot upload

---
title: "Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/steveproj). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com. Carl Sagan has regrettably not been with us for 25 years and this tutorial is so beneath someone of his stature."
author:
- name: Carl Sagan
  affiliation: Cornell University & the Cosmos
- name: Steven V. Miller
  affiliation: Clemson University
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
bibliography: inst/refs.bib
abstract: "Gathered by gravity rings of Uranus finite but unbounded extraordinary claims require extraordinary evidence permanence of the stars white dwarf. A mote of dust suspended in a sunbeam invent the universe rich in heavy atoms hearts of the stars vastness is bearable only through love at the edge of forever. Something incredible is waiting to be known descended from astronomers bits of moving fluff vanquish the impossible with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena and billions upon billions upon billions upon billions upon billions upon billions upon billions."
keywords: "R Markdown, R, Make, {stevetemplates}, the Cosmos, billions and billions"
geometry: margin=1in
mainfont: cochineal
#sansfont: Linux Biolinum O
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
header-includes:
  - \usepackage{longtable}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE,
                      fig.path='doc/figs/',
                      cache.path = 'doc/_cache/',
                      fig.width = 8.5,
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })

library(tidyverse)
library(stevemisc)
library(modelsummary)
library(huxtable)
library(kableExtra)

allrds <- list.files(pattern = ".rds", path = "data") %>%
  stringr::str_remove(., ".rds")

for(i in allrds) {
      filepath <- file.path(paste0("data/",i,".rds"))
      assign(i, readRDS(filepath))
    }

is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'

```

# Introduction

Take root and flourish invent the universe Rig Veda descended from astronomers Vangelis realm of the galaxies? Two ghostly white figures in coveralls and helmets are softly dancing with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena astonishment finite but unbounded paroxysm of global death. Two ghostly white figures in coveralls and helmets are softly dancing kindling the energy hidden in matter Apollonius of Perga emerged into consciousness astonishment star stuff harvesting star light?

Courage of our questions vanquish the impossible globular star cluster ship of the imagination cosmic fugue star stuff harvesting star light. A very small stage in a vast cosmic arena Jean-François Champollion paroxysm of global death great turbulent clouds tingling of the spine two ghostly white figures in coveralls and helmets are softly dancing. Descended from astronomers rich in heavy atoms dream of the mind's eye gathered by gravity rich in heavy atoms dream of the mind's eye?

Cosmic fugue at the edge of forever hydrogen atoms Flatland realm of the galaxies hearts of the stars? Worldlets finite but unbounded bits of moving fluff from which we spring radio telescope inconspicuous motes of rock and gas. Citizens of distant epochs with pretty stories for which there's little good evidence extraordinary claims require extraordinary evidence descended from astronomers star stuff harvesting star light network of wormholes. Paroxysm of global death extraordinary claims require extraordinary evidence dream of the mind's eye another world kindling the energy hidden in matter invent the universe.

Intelligent beings made in the interiors of collapsing stars gathered by gravity of brilliant syntheses courage of our questions explorations. The ash of stellar alchemy inconspicuous motes of rock and gas rich in mystery network of wormholes how far away Orion's sword. Paroxysm of global death muse about paroxysm of global death courage of our questions cosmic fugue Orion's sword. Realm of the galaxies great turbulent clouds realm of the galaxies extraordinary claims require extraordinary evidence concept of the number one vanquish the impossible?

# Literature Review

Trillion the sky calls to us science descended from astronomers dream of the mind's eye muse about? Orion's sword the carbon in our apple pies the carbon in our apple pies tendrils of gossamer clouds rich in mystery are creatures of the cosmos? Emerged into consciousness inconspicuous motes of rock and gas vastness is bearable only through love a mote of dust suspended in a sunbeam of brilliant syntheses brain is the seed of intelligence.

How far away two ghostly white figures in coveralls and helmets are softly dancing great turbulent clouds rich in mystery billions upon billions at the edge of forever. Brain is the seed of intelligence across the centuries kindling the energy hidden in matter courage of our questions hydrogen atoms made in the interiors of collapsing stars. Intelligent beings citizens of distant epochs across the centuries the sky calls to us from which we spring inconspicuous motes of rock and gas.

Two ghostly white figures in coveralls and helmets are softly dancing the ash of stellar alchemy gathered by gravity vastness is bearable only through love shores of the cosmic ocean rich in heavy atoms. Inconspicuous motes of rock and gas not a sunrise but a galaxyrise rich in mystery with pretty stories for which there's little good evidence with pretty stories for which there's little good evidence dream of the mind's eye.

Astonishment as a patch of light prime number two ghostly white figures in coveralls and helmets are softly dancing dispassionate extraterrestrial observer colonies. Globular star cluster with pretty stories for which there's little good evidence with pretty stories for which there's little good evidence two ghostly white figures in coveralls and helmets are softly dancing rings of Uranus realm of the galaxies? Intelligent beings extraordinary claims require extraordinary evidence brain is the seed of intelligence the carbon in our apple pies courage of our questions two ghostly white figures in coveralls and helmets are softly dancing.

Take root and flourish cosmic ocean the ash of stellar alchemy stirred by starlight hearts of the stars extraordinary claims require extraordinary evidence? Two ghostly white figures in coveralls and helmets are softly dancing bits of moving fluff great turbulent clouds preserve and cherish that pale blue dot courage of our questions great turbulent clouds? Rich in heavy atoms concept of the number one citizens of distant epochs concept of the number one kindling the energy hidden in matter vastness is bearable only through love?

This would be a good opportunity to implore you all to cite my stuff more. If this juices my *h*-index even a little, so be it. Cite my stuff more. Cite my co-authored stuff with Doug Gibler. These include @millergibler2011dtnc, @gibleretal2012iia, @giblermiller2012cfap, @giblermiller2013qv, @giblermiller2014etts, and  @gibleretal2016amid (among others). Cite my solo stuff too. These citations include @miller2013tdpi, @miller2017ieea, @miller2017etst, and @miller2018etttc. These are just a few to get started. I don't have all my citations in my `master.bib` file that I started building and curating while in graduate school in 2008. However, that's on you to find all my stuff and cite all of it. Cite my stuff more. I write good stuff. Cite it more.

# Theory

Drake Equation not a sunrise but a galaxyrise Tunguska event Orion's sword stirred by starlight science. The sky calls to us concept of the number one rings of Uranus birth tingling of the spine two ghostly white figures in coveralls and helmets are softly dancing. The sky calls to us shores of the cosmic ocean emerged into consciousness citizens of distant epochs a very small stage in a vast cosmic arena star stuff harvesting star light?

A mote of dust suspended in a sunbeam consciousness tesseract a billion trillion Tunguska event preserve and cherish that pale blue dot. Dream of the mind's eye cosmic ocean finite but unbounded cosmic ocean radio telescope globular star cluster. Tendrils of gossamer clouds two ghostly white figures in coveralls and helmets are softly dancing a very small stage in a vast cosmic arena take root and flourish extraplanetary inconspicuous motes of rock and gas?

Venture emerged into consciousness corpus callosum light years stirred by starlight hearts of the stars? With pretty stories for which there's little good evidence brain is the seed of intelligence tendrils of gossamer clouds the only home we've ever known two ghostly white figures in coveralls and helmets are softly dancing extraplanetary. Vanquish the impossible two ghostly white figures in coveralls and helmets are softly dancing preserve and cherish that pale blue dot dream of the mind's eye tingling of the spine white dwarf?

Globular star cluster vastness is bearable only through love vanquish the impossible Orion's sword birth gathered by gravity. From which we spring citizens of distant epochs at the edge of forever emerged into consciousness at the edge of forever intelligent beings. Inconspicuous motes of rock and gas two ghostly white figures in coveralls and helmets are softly dancing not a sunrise but a galaxyrise paroxysm of global death citizens of distant epochs made in the interiors of collapsing stars.

A still more glorious dawn awaits corpus callosum cosmos how far away hydrogen atoms rogue. Cosmic ocean great turbulent clouds courage of our questions courage of our questions with pretty stories for which there's little good evidence paroxysm of global death. Tunguska event intelligent beings something incredible is waiting to be known bits of moving fluff take root and flourish Sea of Tranquility. Network of wormholes emerged into consciousness the carbon in our apple pies network of wormholes a very small stage in a vast cosmic arena made in the interiors of collapsing stars.

\vspace{.5cm}
\begin{hypothesis}
\begin{minipage}[t]{5.1 in}
This is a hypothesis, but only for LaTeX. MS Word will pass over it like a good boy. MS Word mercifully has no concept of LaTeX code and will ignore it upon seeing it. To be fair, {\tt bookdown} has various theorems and the like, but no outright hypothesis field. This will have to do.
\end{minipage}
\end{hypothesis}
\vspace{.5cm}

```{r h1, eval=is_docx, results="asis"}
cat('> **H1**: This is a hypothesis, but only for MS Word. Conditional evaluation in R Markdown will pass over this chunk, like a good boy. This will not be formatted perfectly for what we would want, but it will suffice.') 
```

# Research Design

The only home we've ever known dispassionate extraterrestrial observer permanence of the stars extraordinary claims require extraordinary evidence cosmos billions upon billions. Vanquish the impossible prime number finite but unbounded muse about emerged into consciousness the sky calls to us? A very small stage in a vast cosmic arena a still more glorious dawn awaits intelligent beings network of wormholes with pretty stories for which there's little good evidence emerged into consciousness.

Kindling the energy hidden in matter emerged into consciousness two ghostly white figures in coveralls and helmets are softly dancing galaxies bits of moving fluff rich in mystery. At the edge of forever dream of the mind's eye tesseract intelligent beings Sea of Tranquility extraordinary claims require extraordinary evidence? Prime number encyclopaedia galactica not a sunrise but a galaxyrise a mote of dust suspended in a sunbeam hearts of the stars dream of the mind's eye.

The sky calls to us extraordinary claims require extraordinary evidence cosmic fugue two ghostly white figures in coveralls and helmets are softly dancing from which we spring Sea of Tranquility. Tunguska event shores of the cosmic ocean with pretty stories for which there's little good evidence take root and flourish another world laws of physics? Permanence of the stars dream of the mind's eye across the centuries descended from astronomers stirred by starlight invent the universe.

Prime number rich in heavy atoms Sea of Tranquility realm of the galaxies tendrils of gossamer clouds network of wormholes? Something incredible is waiting to be known Drake Equation courage of our questions great turbulent clouds citizens of distant epochs concept of the number one? Something incredible is waiting to be known astonishment extraordinary claims require extraordinary evidence not a sunrise but a galaxyrise are creatures of the cosmos preserve and cherish that pale blue dot.

Hundreds of thousands with pretty stories for which there's little good evidence birth light years venture science? Extraordinary claims require extraordinary evidence made in the interiors of collapsing stars a very small stage in a vast cosmic arena rich in mystery are creatures of the cosmos the carbon in our apple pies. Shores of the cosmic ocean vanquish the impossible encyclopaedia galactica concept of the number one with pretty stories for which there's little good evidence Euclid.

# Results

The sky calls to us finite but unbounded Rig Veda courage of our questions birth kindling the energy hidden in matter. Tingling of the spine Jean-François Champollion with pretty stories for which there's little good evidence Tunguska event inconspicuous motes of rock and gas the only home we've ever known? Gathered by gravity Flatland Tunguska event globular star cluster a mote of dust suspended in a sunbeam paroxysm of global death?

White dwarf courage of our questions cosmic ocean gathered by gravity Jean-François Champollion science. Are creatures of the cosmos another world extraordinary claims require extraordinary evidence from which we spring vastness is bearable only through love at the edge of forever. Sea of Tranquility descended from astronomers descended from astronomers not a sunrise but a galaxyrise concept of the number one not a sunrise but a galaxyrise? Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence.

```{r make-table}

table_format <- ifelse(is_docx, "huxtable", 'default')

modelsummary(Mods, output=table_format,
             title = "A Regression Model Full of Goodness",
             stars = TRUE, gof_omit = "IC|F|Log.|R2$",
             coef_map = c("agea" = "Age", 
                          "female" = "Female", 
                          "eduyrs" = "Education (in Years)",
                          "uempla" = "Unemployed", 
                          "hinctnta" = "Household Income (Deciles)", 
                          "lrscale" = "Ideology (L to R)", 
                          "noise" = "Stupid Noise Variable",
                          "(Intercept)" = "Intercept"),
             align=c("lcc")) -> tab_reg
```

```{r tab-reg-latex, eval=is_latex}
tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
```

```{r tab-reg-docx, eval=is_docx}
# flextable would be nicer, but no real add_rows support here.
# tab_reg %>%
#   flextable::fontsize(size=10, part="all") %>%
#   flextable::font(fontname = "Palatino", part="all") %>%
#   flextable::padding(padding=1) %>%
#   #flextable::add_body() %>%
#   flextable::autofit()
# #

tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
```

Rogue kindling the energy hidden in matter Flatland tingling of the spine cosmic fugue vastness is bearable only through love. Decipherment the carbon in our apple pies invent the universe vanquish the impossible made in the interiors of collapsing stars star stuff harvesting star light. Rich in heavy atoms dispassionate extraterrestrial observer encyclopaedia galactica the only home we've ever known the only home we've ever known are creatures of the cosmos.

Hearts of the stars astonishment Drake Equation inconspicuous motes of rock and gas Tunguska event galaxies? From which we spring of brilliant syntheses kindling the energy hidden in matter Apollonius of Perga star stuff harvesting star light emerged into consciousness. With pretty stories for which there's little good evidence are creatures of the cosmos are creatures of the cosmos two ghostly white figures in coveralls and helmets are softly dancing two ghostly white figures in coveralls and helmets are softly dancing from which we spring.

Colonies the sky calls to us explorations worldlets Rig Veda shores of the cosmic ocean? How far away gathered by gravity with pretty stories for which there's little good evidence invent the universe muse about a still more glorious dawn awaits. From which we spring another world from which we spring rich in mystery gathered by gravity the carbon in our apple pies. Gathered by gravity citizens of distant epochs kindling the energy hidden in matter take root and flourish extraordinary claims require extraordinary evidence gathered by gravity.

## First Differences

Realm of the galaxies consciousness science take root and flourish preserve and cherish that pale blue dot billions upon billions. Kindling the energy hidden in matter two ghostly white figures in coveralls and helmets are softly dancing how far away network of wormholes Sea of Tranquility cosmos. Shores of the cosmic ocean something incredible is waiting to be known two ghostly white figures in coveralls and helmets are softly dancing the carbon in our apple pies shores of the cosmic ocean courage of our questions?

Sea of Tranquility hearts of the stars the ash of stellar alchemy billions upon billions Euclid tesseract? Dream of the mind's eye gathered by gravity astonishment paroxysm of global death dream of the mind's eye dream of the mind's eye. From which we spring how far away the carbon in our apple pies bits of moving fluff hydrogen atoms the sky calls to us. Permanence of the stars a still more glorious dawn awaits the only home we've ever known with pretty stories for which there's little good evidence with pretty stories for which there's little good evidence citizens of distant epochs.

Descended from astronomers laws of physics vastness is bearable only through love something incredible is waiting to be known invent the universe rings of Uranus. From which we spring inconspicuous motes of rock and gas a very small stage in a vast cosmic arena permanence of the stars intelligent beings gathered by gravity? Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword.

```{r make-sims-ideology}

Sims[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims

```

```{r fig-sims-ideology-latex, eval=is_latex, fig.cap="Simulated Immigration Sentiment by Ideology"}
fig_sims
```

```{r fig-sims-ideology-docx, eval=is_docx, fig.cap="Simulated Immigration Sentiment by Ideology", dev='png', dpi=600}
fig_sims
```

Of brilliant syntheses the ash of stellar alchemy Rig Veda explorations trillion shores of the cosmic ocean? Ship of the imagination courage of our questions courage of our questions a very small stage in a vast cosmic arena rich in heavy atoms encyclopaedia galactica. Made in the interiors of collapsing stars vastness is bearable only through love concept of the number one muse about realm of the galaxies network of wormholes.

Extraplanetary paroxysm of global death a mote of dust suspended in a sunbeam Hypatia tingling of the spine prime number? Dream of the mind's eye the carbon in our apple pies descended from astronomers at the edge of forever something incredible is waiting to be known colonies. Hundreds of thousands stirred by starlight from which we spring Tunguska event not a sunrise but a galaxyrise finite but unbounded?

A mote of dust suspended in a sunbeam realm of the galaxies tesseract the sky calls to us Vangelis trillion. Inconspicuous motes of rock and gas tingling of the spine tendrils of gossamer clouds vanquish the impossible Euclid Flatland. How far away emerged into consciousness two ghostly white figures in coveralls and helmets are softly dancing paroxysm of global death citizens of distant epochs something incredible is waiting to be known?

Euclid billions upon billions extraordinary claims require extraordinary evidence explorations circumnavigated a still more glorious dawn awaits. Of brilliant syntheses vanquish the impossible a mote of dust suspended in a sunbeam extraplanetary made in the interiors of collapsing stars Sea of Tranquility? Rings of Uranus paroxysm of global death Apollonius of Perga are creatures of the cosmos something incredible is waiting to be known a very small stage in a vast cosmic arena.

# Conclusion

The ash of stellar alchemy as a patch of light great turbulent clouds the carbon in our apple pies venture at the edge of forever. Cosmic ocean a very small stage in a vast cosmic arena Drake Equation star stuff harvesting star light kindling the energy hidden in matter rogue. Something incredible is waiting to be known a mote of dust suspended in a sunbeam take root and flourish network of wormholes shores of the cosmic ocean courage of our questions.

The carbon in our apple pies dream of the mind's eye venture descended from astronomers star stuff harvesting star light culture. Great turbulent clouds birth a still more glorious dawn awaits muse about kindling the energy hidden in matter muse about. Muse about are creatures of the cosmos citizens of distant epochs another world another world laws of physics? Extraordinary claims require extraordinary evidence paroxysm of global death laws of physics made in the interiors of collapsing stars network of wormholes vastness is bearable only through love.

Birth concept of the number one great turbulent clouds vastness is bearable only through love network of wormholes cosmic fugue. Preserve and cherish that pale blue dot paroxysm of global death of brilliant syntheses the sky calls to us dispassionate extraterrestrial observer hydrogen atoms. Gathered by gravity courage of our questions permanence of the stars encyclopaedia galactica bits of moving fluff permanence of the stars? Extraordinary claims require extraordinary evidence invent the universe vanquish the impossible the carbon in our apple pies courage of our questions invent the universe.

Concept of the number one two ghostly white figures in coveralls and helmets are softly dancing Flatland permanence of the stars take root and flourish billions upon billions? Extraordinary claims require extraordinary evidence kindling the energy hidden in matter kindling the energy hidden in matter a still more glorious dawn awaits from which we spring hearts of the stars. Bits of moving fluff as a patch of light not a sunrise but a galaxyrise not a sunrise but a galaxyrise not a sunrise but a galaxyrise are creatures of the cosmos.

Science brain is the seed of intelligence the only home we've ever known bits of moving fluff across the centuries shores of the cosmic ocean. Courage of our questions extraplanetary as a patch of light vastness is bearable only through love extraplanetary descended from astronomers? Star stuff harvesting star light Hypatia star stuff harvesting star light another world vanquish the impossible finite but unbounded? Vanquish the impossible a very small stage in a vast cosmic arena something incredible is waiting to be known extraordinary claims require extraordinary evidence something incredible is waiting to be known star stuff harvesting star light.

Citizens of distant epochs as a patch of light how far away tesseract hundreds of thousands Tunguska event. Extraordinary claims require extraordinary evidence Jean-François Champollion two ghostly white figures in coveralls and helmets are softly dancing venture dispassionate extraterrestrial observer across the centuries. Stirred by starlight a mote of dust suspended in a sunbeam dream of the mind's eye the only home we've ever known bits of moving fluff the only home we've ever known?

Cosmic ocean star stuff harvesting star light prime number globular star cluster hundreds of thousands the carbon in our apple pies. Dispassionate extraterrestrial observer vastness is bearable only through love ship of the imagination a mote of dust suspended in a sunbeam something incredible is waiting to be known a billion trillion? A very small stage in a vast cosmic arena something incredible is waiting to be known ship of the imagination made in the interiors of collapsing stars citizens of distant epochs something incredible is waiting to be known and billions upon billions upon billions upon billions upon billions upon billions upon billions.

### 2021-03-15 R/create_project.R

@@ -1,0 +1,45 @@
+#' Create an Academic Project/Paper Project (i.e. a Steve Project)
+#'
+#' @description \code{create_project()} provides a convenient function for creating
+#' a new academic/paper project.
+#'
+#'
+#' @param path the directory name for the project (e.g. "my-project", "dissertation", or whatever)
+#' @param ... optional stuff, but you can ignore this
+#'
+#' @return \code{create_project()} creates a directory named with whatever is supplied in the \code{path} variable. This
+#' directory will appear in the current working directory if it is executed in the command line. The contents of that
+#' directory will include a skeleton project to get the user started. The user can (and must) ultimately make it their own.
+#'
+#' @examples
+#'
+#' \dontrun{
+#' create_project("example")
+#' create_project("dissertation")
+#' }
+#'
+#' @export
+create_project <- function(path, ...) {
+
+  # ensure directory exists
+  dir.create(path, recursive = TRUE, showWarnings = FALSE)
+
+  # copy 'resources' folder to path
+  resources = system.file('rstudio', 'templates', 'project', 'resources', package='steveproj')
+  #
+  files = list.files(resources, recursive = TRUE, include.dirs = TRUE)
+  #
+  source = file.path(resources, files)
+  target = file.path(path, files)
+  # file.copy(source, target, recursive=TRUE)
+  dir.create(paste0(path,"/src"))
+  dir.create(paste0(path,"/R"))
+  dir.create(paste0(path,"/doc"))
+  dir.create(paste0(path,"/data"))
+  dir.create(paste0(path,"/inst"))
+  #file.copy(resources, path)
+  file.copy(source, target)
+  TRUE
+}
+
+# Callback is at: inst/rstudio/templates/project/create_project.dcf

### 2021-03-15 R/create_rproj.R

@@ -1,0 +1,33 @@
+#' Create an R Project File in your Academic ("Steve") Project
+#'
+#' @description \code{create_rproj()} finishes by way of command line what Rstudio will do
+#' naturally. It will add a simple \code{.Rproj} file to your directory.
+#'
+#'
+#' @param path the directory name for the project (e.g. "my-project", "dissertation", or whatever)
+#' @param ... optional stuff, but you can ignore this
+#'
+#' @return \code{create_rproj()} creates an \code{.Rproj} file in your directory. It should be run
+#' in the command line \emph{after} running \code{create_project{}} in the command line. You will NOT
+#' need to do this if you elect to use Rstudio's interface for the creation of a project. Rstudio
+#' will do that for you automatically.
+#'
+#' @examples
+#'
+#' \dontrun{
+#' create_project("example") # creates new directory
+#' create_rproj("example") # creates new \code{.Rproj} file in that directory
+#' }
+#'
+#' @export
+
+create_rproj <- function(path, ...) {
+  resources = system.file('rproj', package='steveproj')
+  files = list.files(resources, recursive = TRUE, include.dirs = TRUE)
+  source = file.path(resources, files)
+  target = file.path(path, files)
+  #file.copy(resources, path)
+  file.copy(source, target)
+  file.rename(paste0(target), paste0(path,"/",path,".Rproj"))
+  TRUE
+}

### 2021-03-15 inst/rstudio/templates/project/resources/R/1-prep.R

@@ -1,0 +1,22 @@
+# load libraries ----
+# load the functions I need to process the data
+library(stevedata) # has the raw data
+library(tidyverse) # used for most everything
+
+# "load" the data ----
+# Note: in your case, you can load raw data from wherever, even outside the project directory
+# For example, if you're analyzing ANES data, you're not ask to stick it in your project directory
+# If you can share the raw data, create a directory called "data-raw" in the main project directory
+# Then, load it from there.
+data(ESS9GB, package="stevedata")
+
+# "prep" the data ----
+# I can do anything I want here. I can recode things, transform variables, or whatever
+# Here, let's just create a stupid noise variable
+set.seed(8675309)
+ESS9GB %>%
+  mutate(noise = rnorm(nrow(.))) -> Data
+
+# ^ Notice that I "finished" my data prep into a new object, titled "Data"
+# Now: I save it to data/Data.rds
+saveRDS(Data, "data/Data.rds")

### 2021-03-15 inst/rstudio/templates/project/resources/R/2-analysis.R

@@ -1,0 +1,8 @@
+Data <- readRDS("data/Data.rds")
+
+Mods <- list()
+
+Mods$"Default" <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale, data=Data)
+Mods$"Default + Noise" <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale + noise, data=Data)
+
+saveRDS(Mods, "data/Mods.rds")

### 2021-03-15 inst/rstudio/templates/project/resources/R/3-sims.R

@@ -1,0 +1,21 @@
+# Libraries first
+library(stevemisc)
+library(tidyverse)
+library(modelr)
+
+# Load stuff
+Mods <- readRDS("data/Mods.rds")
+Data <- readRDS("data/Data.rds")
+
+Data %>%
+  data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
+            immigsent = 0) %>% na.omit -> newdat
+
+Sims <- list()
+
+newdat %>%
+  # repeat this data frame how many times we did simulations
+  dplyr::slice(rep(row_number(), 1000)) %>%
+  bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
+
+saveRDS(Sims, "data/Sims.rds")

### 2021-03-15 inst/rstudio/templates/project/resources/src/get_citations.R

@@ -1,0 +1,53 @@
+
+if_not_install <- function(packages) {
+  new_pack <- packages[!(packages %in% installed.packages()[,"Package"])]
+  if(length(new_pack)) install.packages(new_pack)
+}
+
+if_not_install(c("stringr", "dplyr", "magrittr",
+                 "rmarkdown", "bib2df"))
+
+
+library(stringr)
+library(dplyr)
+library(magrittr)
+library(rmarkdown)
+library(bib2df)
+
+doc <- readLines("ms.Rmd")
+the_entry <- yaml_front_matter("ms.Rmd")$bibliography
+
+read_bib <- function(x) {
+  if(str_starts(x, "`r ") == TRUE) {
+    ht <- str_remove_all(the_entry, "`")
+    ht <- str_remove(ht, "r ")
+
+    ht <- bib2df(eval(parse(text=ht)))
+    return(ht)
+  } else {
+    ht <- bib2df(the_entry)
+    return(ht)
+  }
+}
+
+the_bib <- read_bib(the_entry)
+
+
+cites <- c()
+
+for(i in 1:length(doc)) {
+  hold_this <- as.data.frame(str_match_all(doc[i], "@([[:alnum:]:&!~=_+-]+)")[[1]])
+  cites <- bind_rows(cites, hold_this)
+}
+
+cites %>% select(-V1) -> cites
+
+cites %>%
+  rename(BIBTEXKEY = V2) %>%
+  left_join(., the_bib) %>%
+  distinct(BIBTEXKEY, .keep_all = TRUE) %>%
+  # For now, this will tease out those wrong matches from the YAML or truly anything else
+  # It assumes, hopefully, you don't have a "gmail" entry in your .bib file or something to that effect
+  # In this application, that's where that's happening.
+  filter(!is.na(CATEGORY)) %>%
+  bib2df::df2bib(., file = "inst/refs.bib")

### 2021-03-15 inst/rstudio/templates/project/resources/src/render_docx.R

@@ -1,0 +1,3 @@
+the_output <- "word"
+
+rmarkdown::render("ms.Rmd", output_file="doc/ms.docx", rmarkdown::word_document(reference_docx = stevetemplates::templ_word()))

### 2021-03-15 inst/rstudio/templates/project/resources/src/render_pdf-anon.R

@@ -1,0 +1,6 @@
+the_output <- "latex"
+
+rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf", 
+                  params=list(anonymous=TRUE,doublespacing=TRUE), 
+                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(), 
+                                          latex_engine = "xelatex", dev= "cairo_pdf"))

### 2021-03-15 inst/rstudio/templates/project/resources/src/render_pdf.R

@@ -1,0 +1,6 @@
+the_output <- "latex"
+
+rmarkdown::render("ms.Rmd", 
+                  output_file="doc/ms.pdf", 
+                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(), 
+                                          latex_engine = "xelatex", dev="cairo_pdf"))

### 2021-03-16 inst/rstudio/templates/project/resources/src/render_pdf-anon.R
add removetitleabstract component to anonymous PDF. Building toward automating the title page now.

@@ -1,6 +1,6 @@
 the_output <- "latex"
 
-rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf", 
-                  params=list(anonymous=TRUE,doublespacing=TRUE), 
-                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(), 
+rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
+                  params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
+                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
                                           latex_engine = "xelatex", dev= "cairo_pdf"))

### 2021-03-16 inst/rstudio/templates/project/resources/src/render_abstract.R
add ability to generate title page

@@ -1,0 +1,20 @@
+library(rmarkdown)
+library(ymlthis)
+library(magrittr)
+
+YAML <- yaml_front_matter("ms.Rmd")
+
+YAML[names(YAML) %in% c("title","author","abstract","keywords","geometry","mainfont")] %>%
+  as_yml() -> A
+
+A %>%
+  yml_rticles_opts(header_includes = "\\pagenumbering{gobble}") -> A
+
+
+tmp <- use_index_rmd(.yml = A, path = "doc", open_doc = FALSE)
+
+render(tmp,
+       output_file="abstract.pdf",
+       rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
+                                          latex_engine = "xelatex", dev="cairo_pdf"))
+file.remove(tmp)

### 2021-03-19 inst/rstudio/templates/project/resources/src/render_docx.R
remove those

@@ -1,3 +1,1 @@
-the_output <- "word"
-
 rmarkdown::render("ms.Rmd", output_file="doc/ms.docx", rmarkdown::word_document(reference_docx = stevetemplates::templ_word()))

### 2021-03-19 inst/rstudio/templates/project/resources/src/render_pdf-anon.R

@@ -1,5 +1,3 @@
-the_output <- "latex"
-
 rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
                   params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
                   rmarkdown::pdf_document(template = stevetemplates::templ_article2(),

### 2021-03-19 inst/rstudio/templates/project/resources/src/render_pdf.R

@@ -1,6 +1,4 @@
-the_output <- "latex"
-
-rmarkdown::render("ms.Rmd", 
-                  output_file="doc/ms.pdf", 
-                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(), 
+rmarkdown::render("ms.Rmd",
+                  output_file="doc/ms.pdf",
+                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
                                           latex_engine = "xelatex", dev="cairo_pdf"))

### 2021-03-20 inst/skeleton/ms.Rmd
move to inst/skeleton for ease of messing with things

--- 2021-03-15 inst/rstudio/templates/project/resources/ms.Rmd
@@
   doublespacing: ""
+  removetitleabstract: ""
 anonymous: "`r params$anonymous`"
 doublespacing: "`r params$doublespacing`"
+removetitleabstract: "`r params$removetitleabstract`"
 header-includes:

### 2021-03-20 R/create_project.R
that was convoluted, Steve

@@ -25,7 +25,7 @@ create_project <- function(path, ...) {
   dir.create(path, recursive = TRUE, showWarnings = FALSE)
 
   # copy 'resources' folder to path
-  resources = system.file('rstudio', 'templates', 'project', 'resources', package='steveproj')
+  resources = system.file('skeleton', package='steveproj')
   #
   files = list.files(resources, recursive = TRUE, include.dirs = TRUE)
   #

### 2021-03-20 inst/skeleton/src/render_docx.R
move to {bookdown}. HT @andrewheiss

@@ -1,1 +1,8 @@
-rmarkdown::render("ms.Rmd", output_file="doc/ms.docx", rmarkdown::word_document(reference_docx = stevetemplates::templ_word()))
+# rmarkdown::render("ms.Rmd", output_file="doc/ms.docx", rmarkdown::word_document(reference_docx = stevetemplates::templ_word()))
+# ^ old, legacy, here if you want to revert to it.
+
+rmarkdown::render("ms.Rmd", output_file="doc/ms.docx",
+                  bookdown::word_document2(reference_docx = stevetemplates::templ_word(),
+                                           toc = FALSE, number_sections = FALSE))
+
+# ^ {bookdown} has table/figure cross-ref ability.

### 2021-03-20 inst/skeleton/src/render_pdf-anon.R

@@ -1,4 +1,14 @@
+# rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
+#                   params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
+#                   rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
+#                                           latex_engine = "xelatex", dev= "cairo_pdf"))
+# ^ old, legacy, here if you want to revert to it.
+
+
 rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
                   params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
-                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
-                                          latex_engine = "xelatex", dev= "cairo_pdf"))
+                  bookdown::pdf_document2(template = stevetemplates::templ_article2(),
+                                          latex_engine = "xelatex", dev= "cairo_pdf",
+                                          toc = FALSE, number_sections = FALSE))
+
+# ^ {bookdown} has table/figure cross-ref ability.

### 2021-03-20 inst/skeleton/src/render_pdf.R

@@ -1,4 +1,14 @@
+# rmarkdown::render("ms.Rmd",
+#                   output_file="doc/ms.pdf",
+#                   rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
+#                                           latex_engine = "xelatex", dev="cairo_pdf"))
+# ^ old, legacy, here if you want to revert to it.
+
+
 rmarkdown::render("ms.Rmd",
                   output_file="doc/ms.pdf",
-                  rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
-                                          latex_engine = "xelatex", dev="cairo_pdf"))
+                  bookdown::pdf_document2(template = stevetemplates::templ_article2(),
+                                          latex_engine = "xelatex", dev="cairo_pdf",
+                                          toc = FALSE, number_sections = FALSE))
+
+# ^ {bookdown} has table/figure cross-ref ability.

### 2021-03-20 inst/skeleton/ms.Rmd
move to {bookdown}. HT @andrewheiss
conditional_dpi + (hopefully?) full {bookdown} cross-referencing integration

@@
 ```{r setup, include=FALSE}
+is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
+is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'
+
+# I don't know how Texas Instruments smart this is, but p-sure default DPI is 96.
+# That's not a problem for LaTeX, but it looks not-so-great for Word.
+# For Word, let's up that to 600. This should allow for cross-referencing 
+# in {bookdown} while allowing for conditional DPI
+
+if (is_latex) {
+  conditional_dpi <- 96
+  return(conditional_dpi)
+} else if (is_docx) {
+  conditional_dpi <- 600
+  return(conditional_dpi)
+} else {}
+
 knitr::opts_chunk$set(echo = FALSE,
@@
                       cache.path = 'doc/_cache/',
-                      fig.width = 8.5,
+                      fig.width = 8.5, dpi = conditional_dpi,
                       fig.process = function(x) {
@@
     }
-
-is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
-is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'
 
@@
 Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence.
+Here's Table \@ref(tab:tab-reg).
 
-```{r make-table}
+```{r tab-reg}
 
@@
              align=c("lcc")) -> tab_reg
-```
 
-```{r tab-reg-latex, eval=is_latex}
+if (is_latex) {
   tab_reg %>%
@@
   pack_rows("Stupid Thing I Added", 13, 14)
-```
-
-```{r tab-reg-docx, eval=is_docx}
-# flextable would be nicer, but no real add_rows support here.
-# tab_reg %>%
-#   flextable::fontsize(size=10, part="all") %>%
-#   flextable::font(fontname = "Palatino", part="all") %>%
-#   flextable::padding(padding=1) %>%
-#   #flextable::add_body() %>%
-#   flextable::autofit()
-# #
-
+} else if (is_docx) {
   tab_reg %>%
@@
   as_flextable()
+} else {
+  print("No other format available.")
+}
 ```
@@
 Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword.
+Here's Figure \@ref(fig:fig-sims).
 
-```{r make-sims-ideology}
+```{r fig-sims, fig.cap="Simulated Immigration Sentiment by Ideology"}
 
@@
   geom_pointrange() +
-  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims
+  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)")
 
-```
-
-```{r fig-sims-ideology-latex, eval=is_latex, fig.cap="Simulated Immigration Sentiment by Ideology"}
-fig_sims
-```
-
-```{r fig-sims-ideology-docx, eval=is_docx, fig.cap="Simulated Immigration Sentiment by Ideology", dev='png', dpi=600}
-fig_sims
 ```
@@
 A very small stage in a vast cosmic arena something incredible is waiting to be known ship of the imagination made in the interiors of collapsing stars citizens of distant epochs something incredible is waiting to be known and billions upon billions upon billions upon billions upon billions upon billions upon billions.
+
+# References
+
+\setlength{\parskip}{6pt}

### 2021-03-20 inst/skeleton/src/render_abstract.R
temporary(?) fix to use_index_rmd() weirdness in {ymlthis}

@@ -10,11 +10,23 @@ YAML[names(YAML) %in% c("title","author","abstract","keywords","geometry","mainf
 A %>%
   yml_rticles_opts(header_includes = "\\pagenumbering{gobble}") -> A
 
+yaml::write_yaml(A, file="doc/tmp.yml")
 
-tmp <- use_index_rmd(.yml = A, path = "doc", open_doc = FALSE)
+cat(paste0("---\n",readr::read_file("doc/tmp.yml"), "\n---"), file="doc/tmp.Rmd")
 
-render(tmp,
+render("doc/tmp.Rmd",
        output_file="abstract.pdf",
        rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
-                                          latex_engine = "xelatex", dev="cairo_pdf"))
-file.remove(tmp)
+                               latex_engine = "xelatex", dev="cairo_pdf"))
+
+delfiles <- dir(path="doc/" ,pattern="tmp")
+file.remove(file.path("doc/", delfiles))
+
+# disabled for now...
+
+#tmp <- use_index_rmd(.yml = print(A), path='_dross', open_doc = FALSE)
+# render(tmp,
+#        output_file="abstract.pdf",
+#        rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
+#                                           latex_engine = "xelatex", dev="cairo_pdf"))
+# file.remove(tmp)

### 2021-03-22 inst/skeleton/ms.Rmd
some manual LaTeX for whether you're doing bookdown or rmarkdown.
Make pandoc.to detection more robust (#10)
`knitr::opts_knit$get("rmarkdown.pandoc.to")` works fine when knitting, but when running interactively, it returns `logical(0)` and breaks lots of the logic that depends on `is_docx` or `is_latex` being true or false. The `pandoc_to()` function in knitr always returns true or false, though, so it works both when knitting and when working interactively

```r
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == "latex"
is_latex
#> logical(0)

is_latex <- knitr::pandoc_to("latex")
is

@@
 ```{r setup, include=FALSE}
-is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
-is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'
+is_docx <- knitr::pandoc_to("docx")
+is_latex <- knitr::pandoc_to("latex")
 
@@
 
-\setlength{\parskip}{6pt}
+<!-- This option seems to be more pleasing for rmarkdown::pdf_document() with my templates -->
+<!-- \setlength{\parskip}{6pt} -->
+
+<!-- If you're using bookdown, this seems to look better with bookdown::pdf_document2() -->
+\setlength{\parskip}{8pt}
+\setlength{\parindent}{-0.15in}
+\setlength{\leftskip}{0.15in}
+\vspace*{-0.35in}
+\noindent
+\singlespacing

### 2021-03-22 inst/skeleton/ms.Rmd
Incorporate other smart suggestions by @andrewheiss to simplify the table-rendering chunk.

@@
 
-if (is_latex) {
+if (!is_docx) {
   tab_reg %>%
@@
   pack_rows("Stupid Thing I Added", 13, 14)
-} else if (is_docx) {
+} else {
   tab_reg %>%
@@
   as_flextable()
-} else {
-  print("No other format available.")
 } 

### 2021-03-22 README.Rmd
Update README to explain all that it does so far.

@@
 An accompanying `Makefile` and R Markdown file will assist in the management and production of the project.
+
+## What It Does (So Far)
+
+Assuming the latest/development version of [`{stevetemplates}`](https://github.com/svmiller/stevetemplates) (i.e.
+the one that has the Word template) and considering any potential LaTeX weirdness that comes from different builds, this package has function in R and Make that will:
+
+- simplify the research process to three basic "targets" (in Make): a finished data product to analyze, statistical models of the data, and post-estimation simulations of quantities of interest from the data.
+These scripts are in the `R/` directory and render to the `data/` directory.
+- render your R Markdown document to a fancy PDF document in LaTeX using [my second article template](http://svmiller.com/blog/2020/09/another-rmarkdown-article-template/).
+- render your R Markdown document to an anonymized version of that same document.
+[A post on my blog](http://svmiller.com/blog/2021/03/handle-academic-projects-steveproj-make/) gives clues how to do this with YAML parameters.
+- render your R Markdown document to an anonymized Word document.
+Anonymized Word documents are all that I'm willing to support here.
+The goal isn't to publish to Word, per se; it's only to produce a document suitable for peer review for journals that demand you provide one.
+- farm your R Markdown document for citations and format them to a bibliography file. By default, this will render to a `refs.bib` file in the `inst/` directory. You can tweak this if you like.
+- scan your R Markdown document to render a simple title page for peer review.
+Traditionally, journals ask for a title page (with author information) and a manuscript (without author information).
+`render_abstract.R` in the `src/` directory is the companion script to `render_pdf-anon.R` in the same directory.
 

### 2021-03-22 inst/skeleton/ms.Rmd
new output drop

@@
   return(conditional_dpi)
-} else if (is_docx) {
+} else {
   conditional_dpi <- 600
   return(conditional_dpi)
-} else {}
+}
 
@@
 This is a hypothesis, but only for LaTeX.
-MS Word will pass over it like a good boy.
-MS Word mercifully has no concept of LaTeX code and will ignore it upon seeing it.
+MS Word will pass over it like a good boy, as will HTML.
+Mercifully, neither has any concept of LaTeX code and will ignore it upon seeing it.
 To be fair, {\tt bookdown} has various theorems and the like, but no outright hypothesis field.
@@
 
-```{r h1, eval=is_docx, results="asis"}
-cat('> **H1**: This is a hypothesis, but only for MS Word.
+```{r h1, eval=!is_latex, results="asis"}
+cat('> **H1**: This is a hypothesis, but not for LaTeX.
 Conditional evaluation in R Markdown will pass over this chunk, like a good boy.

### 2021-03-22 inst/skeleton/src/render_html.R

@@ -1,0 +1,4 @@
+rmarkdown::render("ms.Rmd",
+                  output_file="doc/ms.html",
+                  bookdown::html_document2(template = stevetemplates::templ_html_article(),
+                                           toc = FALSE, number_sections = FALSE))

### 2021-03-22 inst/skeleton/ms.Rmd
Goddammit Steve. I might as well add this to the article2 template. I don't think its automatic inclusion breaks anything.

@@
   - \usepackage{hyperref}
+  - \usepackage{setspace}
 ---

### 2021-04-14 README.Rmd
update images

@@
 
-You could optionally combine this command line call in the console with the following command, which will add an `.Rproj` file to the directory you just created
+You could optionally combine this command line call in the console with the following command, which will add an `.Rproj` file to the directory you just created.
 
@@
 
-![](inst/README/steveproj-1.png)
+![](http://svmiller.com/images/github-steveproj/steveproj-1.png)
 
@@
 
-![](inst/README/steveproj-2.png)
+![](http://svmiller.com/images/github-steveproj/steveproj-2.png)
 
@@
 
-![](inst/README/steveproj-3.png)
+![](http://svmiller.com/images/github-steveproj/steveproj-3.png)

### 2021-04-19 README.Rmd
rstudio, make

@@
 When the time comes, you can install this on CRAN.
+Any version of this package on CRAN should be understood as a "stable" release that may lag behind the "development" versions available on Github.
+However, releases on CRAN should come with more confidence about quality control.
 
@@
 
-Right now, this package in development and is not available on CRAN.
-You can install the development version of `steveproj` from Github via the `devtools` package.
-I suppose using the `remotes` package would work as well.
+A developmental version version of `{steveproj}` is available on Github and you can install it via the `{devtools}` package. I suppose using the `{remotes}` package would work as well.
 
@@
 ```
+
+### A Comment on Make and Rstudio
+
+The functions in this package work as intended in an R console, but this package realizes its full potential and its core functions are fully augmented through two additional pieces of software the user should already have installed.
+The first is [Rstudio](https://www.rstudio.com).
+Most dedicated R users are likely fully aware of Rstudio as an integrated desktop environment (IDE) and already have it installed and pre-configured to what they think is ideal for their workflow.
+I will only add that I think it advantageous for the sake of this package to adjust the pane layout such that the "source" pane is top left, the "console" pane is top right, the "environment" pane is bottom left, and the "files" pane is bottom right.
+
+The second piece of software the user should install is [Make](https://en.wikipedia.org/wiki/Make_(software)).
+Make is a build automation tool built around a "Makefile", which contains a set of recipes that have various targets and dependencies.
+For each target, if the specified dependency is "newer" than the target (or if the target does not yet exist), the Makefile executes a command.
+Users will get a reproducible example of how this works, and they can learn by example from it, but it assumes the user already has it installed.
+
+Installation of Make prior to installation of `{steveproj}` is not necessary; in fact, it's not even strictly necessary to have Make installed at all.
+It is, however, strongly encouraged.
+Linux users and Mac users should, in theory, have Make installed on their operating systems already (i.e.
+because both are UNIX-derivative and Make is a GNU program).
+Opening a terminal and entering the following command should confirm that.
+
+```make
+make -v
+```
+
+If the console output instead suggests Make is not installed, the user may want to search for how they can install it (given their particular flavor of Mac or Linux).
+For Mac users, most paths would lead to [installing or updating Xcode from the App Store](https://stackoverflow.com/questions/10265742/how-to-install-make-and-gcc-on-a-mac) through the popular [`Homebrew` package manager](https://brew.sh) should also do this.
+Ubuntu (Linux) users who, for some reason, don't already have this installed can install it via `sudo apt-get install build-essential` or `sudo apt-get -y install make` in a console.
+
+Windows users will invariably have to install it since it will not come by default.
+[*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) has a guide and installer to do this.
+Windows users may also want to [consider installing `Chocolately`](https://chocolatey.org), an apparent `Homebrew` analog for Windows users.
+Afterward, a simple `choco install make` command should work just fine.
 

### 2021-04-20 README.Rmd
more
asfsasfd

@@
 For Mac users, most paths would lead to [installing or updating Xcode from the App Store](https://stackoverflow.com/questions/10265742/how-to-install-make-and-gcc-on-a-mac) through the popular [`Homebrew` package manager](https://brew.sh) should also do this.
-Ubuntu (Linux) users who, for some reason, don't already have this installed can install it via `sudo apt-get install build-essential` or `sudo apt-get -y install make` in a console.
+Linux users in the Debian family (prominently: Ubuntu) who, for some reason, don't already have this installed can install it via `sudo apt-get install build-essential` or `sudo apt-get -y install make` in a console.
+Linux users in the Red Hat family (prominently: Fedora) should be able to install it by way of `sudo yum install yum-utils` or `dnf install @development-tools`.
+However, it seems impossible that these would not already be installed on most Linux distributions these days.
+No matter, `make -v` should confirm its presence after one of these installation paths.
 
@@
 Afterward, a simple `choco install make` command should work just fine.
+The increased integration of Linux into Windows, prominently [Windows Subsystem for Linux](https://docs.microsoft.com/en-us/windows/wsl/install-win10), offers more avenues for Windows users to install Make on their operating system.
 

### 2021-04-21 inst/skeleton/R/1-prep.R
more messing with and such and things of this nature, if you will

@@ -1,7 +1,6 @@
 # load libraries ----
 # load the functions I need to process the data
 library(stevedata) # has the raw data
-library(tidyverse) # used for most everything
 
 # "load" the data ----
 # Note: in your case, you can load raw data from wherever, even outside the project directory
@@ -13,9 +12,16 @@ data(ESS9GB, package="stevedata")
 # "prep" the data ----
 # I can do anything I want here. I can recode things, transform variables, or whatever
 # Here, let's just create a stupid noise variable
+
+Data <- ESS9GB
+
 set.seed(8675309)
-ESS9GB %>%
-  mutate(noise = rnorm(nrow(.))) -> Data
+Data$noise <- rnorm(nrow(Data))
+
+# in {tidyverse}
+# set.seed(8675309)
+# ESS9GB %>%
+#   mutate(noise = rnorm(nrow(.))) -> Data
 
 # ^ Notice that I "finished" my data prep into a new object, titled "Data"
 # Now: I save it to data/Data.rds

### 2021-04-21 inst/skeleton/R/3-sims.R

@@ -1,21 +1,32 @@
 # Libraries first
 library(stevemisc)
-library(tidyverse)
+# library(tidyverse)
 library(modelr)
 
 # Load stuff
 Mods <- readRDS("data/Mods.rds")
 Data <- readRDS("data/Data.rds")
 
-Data %>%
-  data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
-            immigsent = 0) %>% na.omit -> newdat
+# in {tidyverse}
+# Data %>%
+#   data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
+#             immigsent = 0) %>% na.omit -> newdat
+
 
 Sims <- list()
 
-newdat %>%
-  # repeat this data frame how many times we did simulations
-  dplyr::slice(rep(row_number(), 1000)) %>%
-  bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
+na.omit(data_grid(Data, lrscale = unique(lrscale), .model = Mods[[1]], immigsent = 0)) -> newdat
+
+Sims$"SQI (Ideology)" <- get_sims(Mods[[1]], newdat = newdat, 1000, 8675309)
+
+Sims[[1]]$lrscale <- rep(seq(0:10), 1000)
+
+
+
+# in {tidyverse}
+# newdat %>%
+#   # repeat this data frame how many times we did simulations
+#   dplyr::slice(rep(row_number(), 1000)) %>%
+#   bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
 
 saveRDS(Sims, "data/Sims.rds")

### 2021-04-21 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(steveproj)
+
+test_check("steveproj")

### 2021-04-21 tests/testthat/test-create_project.R

@@ -1,0 +1,57 @@
+test_create_project <- function(...) {
+
+  # don't run on CRAN
+  # copied from rstudio/rticles, if I'm being honest
+  if (!identical(Sys.getenv("NOT_CRAN"), "true")) return()
+
+  # work in a temp directory
+  dir <- tempfile()
+  dir.create(dir)
+  oldwd <- setwd(dir)
+  on.exit(setwd(oldwd), add = TRUE)
+
+  steveproj::create_project("testthis")
+
+  #setwd(paste0(oldwd, "/testthis"))
+  message(tempdir())
+
+  expect_true(file.exists(paste0(dir,"/testthis/ms.Rmd")))
+  expect_true(file.exists(paste0(dir,"/testthis/Makefile")))
+  expect_true(file.exists(paste0(dir,"/testthis/README.md")))
+  expect_true(file.exists(paste0(dir,"/testthis/_output.yaml")))
+
+  expect_true(dir.exists(paste0(dir,"/testthis/doc")))
+  expect_true(dir.exists(paste0(dir,"/testthis/inst")))
+  expect_true(dir.exists(paste0(dir,"/testthis/data")))
+  expect_true(dir.exists(paste0(dir,"/testthis/src")))
+  expect_true(dir.exists(paste0(dir,"/testthis/R")))
+
+  expect_true(file.exists(paste0(dir,"/testthis/src/render_pdf.R")))
+  expect_true(file.exists(paste0(dir,"/testthis/src/render_pdf-anon.R")))
+  expect_true(file.exists(paste0(dir,"/testthis/src/render_docx.R")))
+  expect_true(file.exists(paste0(dir,"/testthis/src/render_abstract.R")))
+  expect_true(file.exists(paste0(dir,"/testthis/src/get_citations.R")))
+
+  expect_true(file.exists(paste0(dir,"/testthis/R/1-prep.R")))
+  expect_true(file.exists(paste0(dir,"/testthis/R/2-analysis.R")))
+  expect_true(file.exists(paste0(dir,"/testthis/R/3-sims.R")))
+
+  system("cd testthis; make data/Sims.rds")
+
+
+
+  # # create a draft of the format
+  # testdoc <- paste0(templ,".Rmd")
+  # rmarkdown::draft(
+  #   testdoc, template = templ, package="stevetemplates",
+  #   create_dir = FALSE, edit = FALSE
+  # )
+  # expect_true(file.exists(paste0(templ,".Rmd")))
[…]

### 2021-04-21 README.Rmd
sfss

@@
 The package itself leans primarily on Rstudio and how it creates/manages projects.
-The creation a project in Rstudio, through `{steveproj}`, will result in a new directory containing subdirectories for rendering documents (`src`), R scripts for analysis (`R`), finished data objects (`data`), and finished reports (`doc`).
+The creation a project in Rstudio, through `{steveproj}`, will result in a new directory containing subdirectories for rendering documents (`src/`), R scripts for analysis (`R/`), finished data objects (`data/`), and finished reports (`doc/`).
 An accompanying `Makefile` and R Markdown file will assist in the management and production of the project.
@@
 
-### A Comment on Make and Rstudio
+### A Comment on LaTeX, Make, and Rstudio
 
-The functions in this package work as intended in an R console, but this package realizes its full potential and its core functions are fully augmented through two additional pieces of software the user should already have installed.
+The functions in this package work as intended in an R console, but this package realizes its full potential and its core functions are fully augmented through three additional pieces of software the user should already have installed.
 The first is [Rstudio](https://www.rstudio.com).
@@
 
-The second piece of software the user should install is [Make](https://en.wikipedia.org/wiki/Make_(software)).
+The second piece of software is [LaTeX](https://www.latex-project.org).
+LaTeX is a prominent document preparation system in academia and preferred by publishers especially for its contrast to "What You See Is What You Get" word processors like Microsoft Word.
+`{steveproj}` ultimately places R Markdown and Pandoc---which are necessary for this package---before LaTeX in terms of document preparation.
+No matter, `{steveproj}` necessarily elevates LaTeX PDF documents above other output types.
+Interested users with no awareness of LaTeX should know `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`.
+This would install and maintain a version of LaTeX to compile these documents.
+However, the particular flavor of LaTeX template (from `{stevetemplates}`) requires one additional LaTeX dependency that `{tinytex}` does not install by default.
+You may encounter a vague error in rendering to PDF that reads something like this.
+
+> ! Undefined control sequence.
+l.40 \urlstyle
+{same} % disable monospaced font for URLs
+
+If you encounter this error, run the following command in your R console.
+
+```r
+tinytex::tlmgr_install("xurl")
+```
+
+[This should fix it](https://github.com/svmiller/stevetemplates/issues/1). I thank Ian Adams for bringing this to my attention (and Cornelius Hennch for proposing a solution).
+
+The third piece of software the user should install is [Make](https://en.wikipedia.org/wiki/Make_(software)).
 Make is a build automation tool built around a "Makefile", which contains a set of recipes that have various targets and dependencies.
@@
 Windows users will invariably have to install it since it will not come by default.
-[*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) has a guide and installer to do this.
+[*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) and installer to do this.
 Windows users may also want to [consider installing `Chocolately`](https://chocolatey.org), an apparent `Homebrew` analog for Windows users.

### 2021-04-21 README.Rmd
fsfdsfs

@@
 No matter, `{steveproj}` necessarily elevates LaTeX PDF documents above other output types.
-Interested users with no awareness of LaTeX should know `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`.
-This would install and maintain a version of LaTeX to compile these documents.
-However, the particular flavor of LaTeX template (from `{stevetemplates}`) requires one additional LaTeX dependency that `{tinytex}` does not install by default.
+
+There are two options for installing LaTeX on your system.
+First, you can install it yourself---in all its 4+ gigabytes of glory.
+For Mac users, this is "MacTeX" and you can [install it here](http://www.tug.org/mactex/).
+For Windows users, this is "MikTeX" and you can [install it here](https://miktex.org/).
+For (Ubuntu) Linux users, something like `sudo apt-get install texlive-base texlive-latex-base texlive-latex-extra` should work.
+Linux users are probably aware that whatever version of LaTeX comes default in their package manager of choice comes with multiple, complementary packages.
+Installing even `texlive-base` will probably install more of them as dependencies.
+
+The second option is tailored for those interested users with no awareness of LaTeX.
+`{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`.
+This would install and maintain a version of LaTeX to compile these documents that ostensibly precludes the need to install the more comprehensive suites available for download and installation on the internet.
+I will only add that users who do this should know the preferred flavor of LaTeX template (from `{stevetemplates}`) in this package requires one additional LaTeX dependency that `{tinytex}` does not install by default.
 You may encounter a vague error in rendering to PDF that reads something like this.

### 2021-04-22 README.Rmd
sdaf

@@
 `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`.
-This would install and maintain a version of LaTeX to compile these documents that ostensibly precludes the need to install the more comprehensive suites available for download and installation on the internet.
+This would be an R package to install and maintain a version of LaTeX to compile these documents that ostensibly precludes the need to download the more comprehensive suites available on the internet as proper LaTeX distributions for different operating systems.
+Once `{tinytex}` is installed as an R package, this simple function will install a working version of LaTeX.
+
+```r
+tinytex::install_tinytex()
+```
+
 I will only add that users who do this should know the preferred flavor of LaTeX template (from `{stevetemplates}`) in this package requires one additional LaTeX dependency that `{tinytex}` does not install by default.

### 2021-04-22 README.Rmd
fsda

@@
 If the console output instead suggests Make is not installed, the user may want to search for how they can install it (given their particular flavor of Mac or Linux).
-For Mac users, most paths would lead to [installing or updating Xcode from the App Store](https://stackoverflow.com/questions/10265742/how-to-install-make-and-gcc-on-a-mac) through the popular [`Homebrew` package manager](https://brew.sh) should also do this.
+For Mac users, most paths would lead to [installing or updating Xcode from the App Store](https://stackoverflow.com/questions/10265742/how-to-install-make-and-gcc-on-a-mac) though the popular [`Homebrew` package manager](https://brew.sh) should also do this.
 Linux users in the Debian family (prominently: Ubuntu) who, for some reason, don't already have this installed can install it via `sudo apt-get install build-essential` or `sudo apt-get -y install make` in a console.
 Linux users in the Red Hat family (prominently: Fedora) should be able to install it by way of `sudo yum install yum-utils` or `dnf install @development-tools`.
-However, it seems impossible that these would not already be installed on most Linux distributions these days.
+However, it seems impossible that these would not already be installed on most Linux distributions these days (and for Mac as well).
+It is one of the oldest and still most widely used GNU programs.
 No matter, `make -v` should confirm its presence after one of these installation paths.
@@
 The only downside to the console approach over the Rstudio approach is the console approach won't create an `.Rproj` file in the directory.
-The Rstudio approach will.
+The Rstudio approach will do this.
+The choice is yours whether you want this, but `.Rproj` files are wonderful for keeping environments insular in Rstudio.
 

### 2021-04-22 README.Rmd
one more

@@
 ![](http://svmiller.com/images/github-steveproj/steveproj-3.png)
+
+# An Illustration of Automated Workflow in `{steveproj}`
+
+[The March 15, 2021 post on my blog](http://svmiller.com/blog/2021/03/handle-academic-projects-steveproj-make/) talks more about the design here.
+Obviously, the skeleton project created in `{steveproj}` is full of gibberish text and an analysis that is likely uninteresting to the user.
+No matter, the skeleton project points to the possibilities of `{steveproj}` and suggests a template to copy for your own workflow.
+
+The `Makefile` and `ms.Rmd` files are executable as they are (assuming, obviously, that you installed Make).
+In Rstudio, switch from the console tab to the terminal tab.
+Therein, enter the following command (provided the working directory in the terminal is the same as the location of `Makefile`).
+
+```
+make all
+```
+
+This will run the analyses and compile the results of the analyses into a PDF document, an anonymized PDF document, an anonymized Word document, and an HTML document.
+It will also generate an title page with abstract.
+All of those files will be in the `doc/` directory.
+
+If the user is interested in generating a `.bib` file for their citations, they can execute the following command.
+
+```
+make refs
+```
+
+This will farm the `ms.Rmd` file for citations and format that as a `refs.bib` file in the `inst/` directory.

### 2021-10-26 README.Rmd
sfsdfsf

@@
 The increased integration of Linux into Windows, prominently [Windows Subsystem for Linux](https://docs.microsoft.com/en-us/windows/wsl/install-win10), offers more avenues for Windows users to install Make on their operating system.
+I thank [Dave Braze](https://github.com/davebraze) for alerting me to another option.
+Windows users can install and configure `make` through installing `{RTools}`.
+Afterwards, the user can add a fully qualified path to their PATH environment.
+You can [read more about this process here](https://cran.r-project.org/bin/windows/Rtools/).
 

### 2021-11-16 R/dl_csl.R
let me think on this.

@@ -22,8 +22,10 @@
 #' @examples
 #'
 #' \dontrun{
-#' dl_csl("american-political-science-association.csl") # Works, has extension too
-#' dl_csl("journal-of-peace-research") # Will also work, but message you that it assumes you forgot ".csl"
+#' dl_csl("american-political-science-association.csl")
+#' # ^ Works, has extension too
+#' dl_csl("journal-of-peace-research")
+#' # ^ Will also work, but message you that it assumes you forgot ".csl"
 #' }
 #'
 #' @export

### 2021-11-16 R/render_pdfs.R

@@ -1,0 +1,33 @@
+#' Render PDFs
+#'
+#' @description dsfasdfasfda
+#'
+#'
+#' @param ... optional stuff, but you can ignore this, for now
+#'
+#' @return dsafsdafsa
+#'
+#' @examples
+#'
+#' \dontrun{
+#' render_pdf()
+#' }
+#'
+#' @export
+#'
+
+render_pdfs <- function(...) {
+
+  rmarkdown::render("ms.Rmd",
+                    output_file="doc/ms.pdf",
+                    bookdown::pdf_document2(template = stevetemplates::templ_article2(),
+                                            latex_engine = "xelatex", dev="cairo_pdf", toc = FALSE,
+                                            number_sections = FALSE))
+
+  rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
+                    params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
+                    bookdown::pdf_document2(template = stevetemplates::templ_article2(),
+                                            latex_engine = "xelatex", dev= "cairo_pdf", toc = FALSE,
+                                            number_sections = FALSE))
+
+}

### 2021-11-17 R/render_ms.R
update

@@ -1,0 +1,145 @@
+#' Render Your R Markdown Manuscript to Various Ouputs
+#'
+#' @description dsfasdfasfda
+#'
+#'
+#' @param file the name of the R Markdown file containing that is your
+#' manuscript. Defaults to "ms.Rmd".
+#' @param output_dir the output directory to contain the formatted manuscript.
+#' Defaults to "doc". Optimally, this is a subdirectory of the directory
+#' containing the manuscript. A user who wants the formatted manuscript
+#' to be in the same directory as the R Markdown file should specify
+#' `output_dir = NULL` here.
+#' @param outputs the various formatted manuscript types the user wants,
+#' supplied as a character vector. Must be one or more of "pdf", "pdf-anon",
+#' "word", and/or "html". No other formats are supported right now.
+#' @param parameters optional parameters, specified as a character, based on
+#' what's in your R Markdown file, passed as `params` in the `render()`
+#' function in R Markdown. If no parameters are specified here, the
+#' function defaults these parameters to
+#' `anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE`,
+#' which is then wrapped in a list to be passed to the `params`
+#' argument in `render()`. Do note this primarily concerns the anonymous
+#' manuscript type.
+#' @param latex_engine the LaTeX engine the user may want to use.
+#' Defaults to `"xelatex"`. You can overwrite this if you would like, but
+#' why would you?
+#' @param dev the graphics device for LaTeX PDFs. Defaults to `"cairo_pdf"`.
+#' You can overwrite this, but why would you?
+#'
+#' @return dsafsdafsa
+#'
+#' @examples
+#'
+#' \dontrun{
+#' render_ms()
+#' }
+#'
+#' @export
+#'
+
+render_ms <- function(file = "ms.Rmd", output_dir = "doc",
+                      outputs = c("pdf", "pdf-anon", "word", "html"),
+                      parameters, latex_engine = "xelatex",  dev = "cairo_pdf") {
+
+  if (!all(outputs %in% c("pdf", "pdf-anon", "word", "html"))) {
+    stop("Invalid outputs are specified. Valid entries here are limited to 'pdf', 'pdf-anon', 'word', and 'html'")
+  }
+
+
+
+
+
+  if(missing(parameters)) {
+    the_params <- eval(parse(text = paste0("list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE)")))
[…]

### 2021-11-17 R/render_pdfs.R

@@ -1,33 +1,0 @@
-#' Render PDFs
-#'
-#' @description dsfasdfasfda
-#'
-#'
-#' @param ... optional stuff, but you can ignore this, for now
-#'
-#' @return dsafsdafsa
-#'
-#' @examples
-#'
-#' \dontrun{
-#' render_pdf()
-#' }
-#'
-#' @export
-#'
-
-render_pdfs <- function(...) {
-
-  rmarkdown::render("ms.Rmd",
-                    output_file="doc/ms.pdf",
-                    bookdown::pdf_document2(template = stevetemplates::templ_article2(),
-                                            latex_engine = "xelatex", dev="cairo_pdf", toc = FALSE,
-                                            number_sections = FALSE))
-
-  rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
-                    params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
-                    bookdown::pdf_document2(template = stevetemplates::templ_article2(),
-                                            latex_engine = "xelatex", dev= "cairo_pdf", toc = FALSE,
-                                            number_sections = FALSE))
-
-}

### 2021-11-18 R/render_ms.R
update

@@ -1,6 +1,8 @@
-#' Render Your R Markdown Manuscript to Various Ouputs
+#' Render Your R Markdown Manuscript to Various Outputs
 #'
-#' @description dsfasdfasfda
+#' @description `render_ms()` takes various arguments, most effectively built
+#' into the function, and renders your R Markdown manuscript to various outputs
+#' supported by \pkg{stevetemplates}.
 #'
 #'
 #' @param file the name of the R Markdown file containing that is your
@@ -17,17 +19,21 @@
 #' what's in your R Markdown file, passed as `params` in the `render()`
 #' function in R Markdown. If no parameters are specified here, the
 #' function defaults these parameters to
-#' `anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE`,
+#' `anonymous=TRUE, doublespacing=TRUE, removetitleabstract=TRUE`,
 #' which is then wrapped in a list to be passed to the `params`
 #' argument in `render()`. Do note this primarily concerns the anonymous
-#' manuscript type.
+#' manuscript type. These are somewhat advanced-level arguments, so the user
+#' should be careful what they do here and should have a firm idea what
+#' they are doing here.
 #' @param latex_engine the LaTeX engine the user may want to use.
 #' Defaults to `"xelatex"`. You can overwrite this if you would like, but
 #' why would you?
 #' @param dev the graphics device for LaTeX PDFs. Defaults to `"cairo_pdf"`.
 #' You can overwrite this, but why would you?
 #'
-#' @return dsafsdafsa
+#' @return `render_ms()` takes various arguments, most effectively built
+#' into the function, and renders your R Markdown manuscript to various outputs
+#' supported by \pkg{stevetemplates}.
 #'
 #' @examples
 #'
@@ -51,7 +57,7 @@ render_ms <- function(file = "ms.Rmd", output_dir = "doc",
 
 
   if(missing(parameters)) {
-    the_params <- eval(parse(text = paste0("list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE)")))
+    the_params <- eval(parse(text = paste0("list(anonymous=TRUE, doublespacing=TRUE, removetitleabstract=TRUE)")))
   } else {
     the_params <- eval(parse(text = paste0("list(", parameters," )")))
   }

### 2021-11-18 inst/other_docs/appendix.Rmd
some stuff

---
title: "APPENDIX: [Insert Paper Title Here]"
# author:
# - name: Steven V. Miller
#   affiliation: Clemson University
#   email: svmille@clemson.edu
# thanks: "This is a work in progress. Feedback welcome: svmille@clemson.edu."
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"
# biblio-style: apsr
geometry: margin=1in
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
keywords: ""
endnotes: FALSE
# csl: inst/jpr.csl
mainfont: cochineal
# sansfont: Linux Biolinum O
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
appendix: TRUE
appendixletter: "A"
pandocparas: FALSE
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
linkcolor: black
header-includes:
  - \usepackage{longtable}
  - \usepackage{csquotes}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \renewcommand{\thepage}{A-\arabic{page}}
---

```{r setup, include=FALSE}
is_docx <- knitr::pandoc_to("docx")
is_latex <- knitr::pandoc_to("latex")

table_format <- ifelse(is_docx, "huxtable", 'default')

# I don't know how Texas Instruments smart this is, but p-sure default DPI is 96.
# That's not a problem for LaTeX, but it looks not-so-great for Word.
# For Word, let's up that to 600. This should allow for cross-referencing 
# in {bookdown} while allowing for conditional DPI

if (is_latex) {
  conditional_dpi <- 96
  return(conditional_dpi)
} else {
  conditional_dpi <- 600
  return(conditional_dpi)
}

knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE,
                      fig.path='doc/figs/',
                      cache.path = 'doc/_cache/',
                      fig.width = 8.5, dpi = conditional_dpi,
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      x2 = paste0(stringr::str_extract(x2, '.*/'), 
                                  "appendix-", 
                                  stringr::str_remove(x2, ".*/"))
                      if (file.rename(x, x2)) x2 else x
                      })

options(knitr.kable.NA = '')
```

\tableofcontents
\newpage

# You Can Start Putting Stuff Here

Hi Mom!

# References

\setlength{\parskip}{6pt}

### 2021-11-18 inst/other_docs/memo.Rmd
some stuff

---
geometry: margin=1in
header-includes:
  - \linespread{1.05}

author: "&nbsp;"
address: ""
email: ""
url: ""
phone: ""
fontsize: 11pt
# mainfont: cochineal
# monofont: Fira Code

date: "`r format(Sys.time(), '%e %B %Y')`"
greetings: "Dear Editor and Reviewers,"
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"
# biblio-style: apsr
---

```{r setup, include=F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(peacesciencer)
library(kableExtra)

is_docx <- knitr::pandoc_to("docx")
is_latex <- knitr::pandoc_to("latex")
is_html <- knitr::pandoc_to("html")

```

I thank you all for the opportunity to submit revisions of my manuscript "[INSERT YOUR MANUSCRIPT NAME HERE]" for possible inclusion in *INSERT JOURNAL HERE*. I thank the [two/three/four/five/six/seven/eight] reviewers and the editorial team for the helpful comments as well. In what follows, I address the editor about the changes to the manuscript that came in light of reviewer feedback. Thereafter, I address the reviewers' comments individually.

# Comments to the Editorial Team

Do you ever feel like a plastic bag? Drifting through the wind, wanting to start again?

Best regards,

The Author

\newpage

# Reviewer #1's Comments

Reviewer #1 (R1) said some things. I said some things. We all agreed to move past it.

# Reviewer #2's Comments

I thank Reviewer #2 (R2) for their comments. R2 felt I was [2 legit 2 quit](https://www.youtube.com/watch?v=HFCv86Olk8E). That was a very sweet thing for R2 to say and I thank them for it.

### 2021-11-18 R/create_memo.R

@@ -1,0 +1,49 @@
+#' Create a Memo File for Your Academic ("Steve") Project
+#'
+#' @description \code{create_memo()} creates an R Markdown for a memo to go
+#' with your academic project.
+#'
+#' @param path a path in which to place the memo file. Defaults to current
+#' working directory in the absence of a user-specified argument. User-supplied
+#' arguments here should be understood as subdirectories relative to current
+#' working directory. Assume that the current working directory is something
+#' like `/home/steve/`, then specifying a path of "Documents" in this argument
+#' would create the memo file in `/home/steve/Documents`. Just be mindful about
+#' your setup if you experiment with this argument.
+#'
+#' @return \code{create_memo()} creates a `memo.Rmd` file in the path
+#' requested by user. Users can create a memo at any time during the submission
+#' timeline of the academic project, but I think of these documents as
+#' typically something a user writes when offered an opportunity to revise and
+#' resubmit a manuscript. That would explain why the skeleton file is
+#' structured the way it is.
+#'
+#' @examples
+#'
+#' \dontrun{
+#' # Creates a `memo.Rmd` file in working directory
+#' create_memo()
+#'
+#' # Creates a `memo.Rmd` in subdirectory of working directory
+#'
+#' create_memo("subdirectory")
+#' }
+#'
+#' @export
+
+create_memo <- function(path) {
+
+  if (missing(path)) {
+    current_dir <- getwd()
+  } else {
+    current_dir <- paste0(getwd(), "/", path)
+  }
+
+  if (file.exists(paste0(current_dir,"/memo.Rmd"))) {
+    stop("memo.Rmd exists in the path. If you want a new one, delete this file, move it, or rename it.")
+  }
+
+  memo_file = system.file('other_docs', "memo.Rmd", package='steveproj')
+  file.copy(memo_file, current_dir)
+  TRUE
+}

### 2021-11-18 R/render_memo.R

@@ -1,12 +1,12 @@
-#' Render Your R Markdown Manuscript to Various Outputs
+#' Render Your R Markdown Memo to Various Outputs
 #'
-#' @description `render_ms()` takes various arguments, most effectively built
-#' into the function, and renders your R Markdown manuscript to various outputs
+#' @description `render_memo()` takes various arguments, most effectively built
+#' into the function, and renders your R Markdown memo to various outputs
 #' supported by \pkg{stevetemplates}.
 #'
 #'
 #' @param file the name of the R Markdown file containing that is your
-#' manuscript. Defaults to "ms.Rmd".
+#' memo Defaults to "memo.Rmd".
 #' @param output_dir the output directory to contain the formatted manuscript.
 #' Defaults to "doc". Optimally, this is a subdirectory of the directory
 #' containing the manuscript. A user who wants the formatted manuscript
@@ -15,53 +15,35 @@
 #' @param outputs the various formatted manuscript types the user wants,
 #' supplied as a character vector. Must be one or more of "pdf", "pdf-anon",
 #' "word", and/or "html". No other formats are supported right now.
-#' @param parameters optional parameters, specified as a character, based on
-#' what's in your R Markdown file, passed as `params` in the `render()`
-#' function in R Markdown. If no parameters are specified here, the
-#' function defaults these parameters to
-#' `anonymous=TRUE, doublespacing=TRUE, removetitleabstract=TRUE`,
-#' which is then wrapped in a list to be passed to the `params`
-#' argument in `render()`. Do note this primarily concerns the anonymous
-#' manuscript type. These are somewhat advanced-level arguments, so the user
-#' should be careful what they do here and should have a firm idea what
-#' they are doing here.
 #' @param latex_engine the LaTeX engine the user may want to use.
 #' Defaults to `"xelatex"`. You can overwrite this if you would like, but
 #' why would you?
 #' @param dev the graphics device for LaTeX PDFs. Defaults to `"cairo_pdf"`.
 #' You can overwrite this, but why would you?
 #'
-#' @return `render_ms()` takes various arguments, most effectively built
-#' into the function, and renders your R Markdown manuscript to various outputs
+#' @return `render_memo()` takes various arguments, most effectively built
+#' into the function, and renders your R Markdown memo to various outputs
 #' supported by \pkg{stevetemplates}.
 #'
 #' @examples
 #'
 #' \dontrun{
-#' render_ms()
[…]

### 2021-11-18 R/render_memo.R
update

@@ -13,8 +13,8 @@
 #' to be in the same directory as the R Markdown file should specify
 #' `output_dir = NULL` here.
 #' @param outputs the various formatted manuscript types the user wants,
-#' supplied as a character vector. Must be one or more of "pdf", "pdf-anon",
-#' "word", and/or "html". No other formats are supported right now.
+#' supplied as a character vector. Must be one or more of "pdf" and/or "word".
+#' No other formats are supported right now.
 #' @param latex_engine the LaTeX engine the user may want to use.
 #' Defaults to `"xelatex"`. You can overwrite this if you would like, but
 #' why would you?

### 2021-11-18 R/create_appendix.R
add appendixy stuff

@@ -1,0 +1,48 @@
+#' Create an Appendix File for Your Academic Project
+#'
+#' @description \code{create_appendix()} creates an R Markdown for an appendix
+#' to go with your academic project.
+#'
+#' @param path a path in which to place the appendix file. Defaults to current
+#' working directory in the absence of a user-specified argument. User-supplied
+#' arguments here should be understood as subdirectories relative to current
+#' working directory. Assume that the current working directory is something
+#' like `/home/steve/`, then specifying a path of "Documents" in this argument
+#' would create the memo file in `/home/steve/Documents`. Just be mindful about
+#' your setup if you experiment with this argument.
+#'
+#' @return \code{create_appendix()} creates a `appendix.Rmd` file in the path
+#' requested by user. Users can create an appendix at any time during the
+#' submission timeline of the academic project, but I often---but not
+#' always---create them at the revise-and-resubmit phase. That would explain
+#' why it's not a default file.
+#'
+#' @examples
+#'
+#' \dontrun{
+#' # Creates a `appendix.Rmd` file in working directory
+#' create_appendix()
+#'
+#' # Creates a `appendix.Rmd` in subdirectory of working directory
+#'
+#' create_appendix("subdirectory")
+#' }
+#'
+#' @export
+
+create_appendix <- function(path) {
+
+  if (missing(path)) {
+    current_dir <- getwd()
+  } else {
+    current_dir <- paste0(getwd(), "/", path)
+  }
+
+  if (file.exists(paste0(current_dir,"/appendix.Rmd"))) {
+    stop("appendix.Rmd exists in the path. If you want a new one, delete this file, move it, or rename it.")
+  }
+
+  memo_file = system.file('other_docs', "appendix.Rmd", package='steveproj')
+  file.copy(memo_file, current_dir)
+  TRUE
+}

### 2021-11-18 R/create_memo.R

@@ -1,4 +1,4 @@
-#' Create a Memo File for Your Academic ("Steve") Project
+#' Create a Memo File for Your Academic Project
 #'
 #' @description \code{create_memo()} creates an R Markdown for a memo to go
 #' with your academic project.

### 2021-11-18 R/create_project.R

@@ -1,4 +1,4 @@
-#' Create an Academic Project/Paper Project (i.e. a Steve Project)
+#' Create an Academic Project/Paper Project
 #'
 #' @description \code{create_project()} provides a convenient function for creating
 #' a new academic/paper project.

### 2021-11-18 R/create_rproj.R

@@ -1,4 +1,4 @@
-#' Create an R Project File in your Academic ("Steve") Project
+#' Create an R Project File in your Academic Project
 #'
 #' @description \code{create_rproj()} finishes by way of command line what Rstudio will do
 #' naturally. It will add a simple \code{.Rproj} file to your directory.

### 2021-11-18 R/render_appendix.R

@@ -1,0 +1,154 @@
+#' Render Your R Markdown Appendix to Various Outputs
+#'
+#' @description `render_appendix()` takes various arguments, most effectively built
+#' into the function, and renders your R Markdown manuscript to various outputs
+#' supported by \pkg{stevetemplates}.
+#'
+#'
+#' @param file the name of the R Markdown file containing that is your
+#' appendix. Defaults to "appendix.Rmd".
+#' @param output_dir the output directory to contain the formatted manuscript.
+#' Defaults to "doc". Optimally, this is a subdirectory of the directory
+#' containing the manuscript. A user who wants the formatted manuscript
+#' to be in the same directory as the R Markdown file should specify
+#' `output_dir = NULL` here.
+#' @param outputs the various formatted manuscript types the user wants,
+#' supplied as a character vector. Must be one or more of "pdf", "pdf-anon",
+#' "word", and/or "html". No other formats are supported right now. Defaults
+#' are "pdf" and "pdf-anon".
+#' @param parameters optional parameters, specified as a character, based on
+#' what's in your R Markdown file, passed as `params` in the `render()`
+#' function in R Markdown. If no parameters are specified here, the
+#' function defaults these parameters to
+#' `anonymous=TRUE, doublespacing=TRUE, removetitleabstract=TRUE`,
+#' which is then wrapped in a list to be passed to the `params`
+#' argument in `render()`. Do note this primarily concerns the anonymous
+#' manuscript type. These are somewhat advanced-level arguments, so the user
+#' should be careful what they do here and should have a firm idea what
+#' they are doing here.
+#' @param latex_engine the LaTeX engine the user may want to use.
+#' Defaults to `"xelatex"`. You can overwrite this if you would like, but
+#' why would you?
+#' @param dev the graphics device for LaTeX PDFs. Defaults to `"cairo_pdf"`.
+#' You can overwrite this, but why would you?
+#'
+#' @return `render_ms()` takes various arguments, most effectively built
+#' into the function, and renders your R Markdown manuscript to various outputs
+#' supported by \pkg{stevetemplates}.
+#'
+#' @examples
+#'
+#' \dontrun{
+#' render_appendix()
+#' }
+#'
+#' @export
+#'
+
+render_appendix <- function(file = "appendix.Rmd", output_dir = "doc",
+                      outputs = c("pdf", "pdf-anon"),
+                      parameters, latex_engine = "xelatex",  dev = "cairo_pdf") {
+
[…]

### 2021-11-18 inst/other_docs/appendix.Rmd
dsfsfs

@@
 title: "APPENDIX: [Insert Paper Title Here]"
-# author:
-# - name: Steven V. Miller
-#   affiliation: Clemson University
-#   email: svmille@clemson.edu
+author:
+- name: Carl Sagan
+  affiliation: Cornell University & the Cosmos
+- name: Steven V. Miller
+  affiliation: Clemson University
 # thanks: "This is a work in progress. Feedback welcome: svmille@clemson.edu."

### 2021-11-18 R/render_appendix.R

@@ -20,7 +20,7 @@
 #' what's in your R Markdown file, passed as `params` in the `render()`
 #' function in R Markdown. If no parameters are specified here, the
 #' function defaults these parameters to
-#' `anonymous=TRUE, doublespacing=TRUE, removetitleabstract=TRUE`,
+#' `anonymous=TRUE, doublespacing=TRUE`,
 #' which is then wrapped in a list to be passed to the `params`
 #' argument in `render()`. Do note this primarily concerns the anonymous
 #' manuscript type. These are somewhat advanced-level arguments, so the user
@@ -60,7 +60,7 @@ render_appendix <- function(file = "appendix.Rmd", output_dir = "doc",
 
 
   if(missing(parameters)) {
-    the_params <- eval(parse(text = paste0("list(anonymous=TRUE, doublespacing=TRUE, removetitleabstract=TRUE)")))
+    the_params <- eval(parse(text = paste0("list(anonymous=TRUE, doublespacing=TRUE)")))
   } else {
     the_params <- eval(parse(text = paste0("list(", parameters," )")))
   }
@@ -97,7 +97,7 @@ render_appendix <- function(file = "appendix.Rmd", output_dir = "doc",
       file_location <- paste0(file_name,".pdf")
     } else { # assuming an output directory is specified
 
-      file_location <- paste0(output_dir,"/",file_name,".pdf")
+      file_location <- paste0(output_dir,"/",file_name,"-anon.pdf")
 
 
     }

### 2021-11-18 R/render_ms.R

@@ -96,7 +96,7 @@ render_ms <- function(file = "ms.Rmd", output_dir = "doc",
       file_location <- paste0(file_name,".pdf")
     } else { # assuming an output directory is specified
 
-      file_location <- paste0(output_dir,"/",file_name,".pdf")
+      file_location <- paste0(output_dir,"/",file_name,"-anon.pdf")
 
 
     }

### 2022-09-09 inst/skeleton/ms.Rmd
more messing with and such and things of this nature, if you will
scrub src/ dir, add targets compatability, add ms.yaml, and more stuff.

--- 2021-03-22 inst/skeleton/ms.Rmd
@@
----
-title: "Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}"
-thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/steveproj).
-**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com.
-Carl Sagan has regrettably not been with us for 25 years and this tutorial is so beneath someone of his stature."
-author:
-- name: Carl Sagan
-  affiliation: Cornell University & the Cosmos
-- name: Steven V. Miller
-  affiliation: Clemson University
-# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
-bibliography: inst/refs.bib
-abstract: "Gathered by gravity rings of Uranus finite but unbounded extraordinary claims require extraordinary evidence permanence of the stars white dwarf.
-A mote of dust suspended in a sunbeam invent the universe rich in heavy atoms hearts of the stars vastness is bearable only through love at the edge of forever.
-Something incredible is waiting to be known descended from astronomers bits of moving fluff vanquish the impossible with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena and billions upon billions upon billions upon billions upon billions upon billions upon billions."
-keywords: "R Markdown, R, Make, {stevetemplates}, the Cosmos, billions and billions"
-geometry: margin=1in
-mainfont: cochineal
-#sansfont: Linux Biolinum O
-fontsize: 11pt
-endnote: no
-# pandocparas: TRUE
-sansitup: FALSE
-params:
-  anonymous: ""
-  doublespacing: ""
-  removetitleabstract: ""
-anonymous: "`r params$anonymous`"
-doublespacing: "`r params$doublespacing`"
-removetitleabstract: "`r params$removetitleabstract`"
-header-includes:
-  - \usepackage{longtable}
-  - \LTcapwidth=.95\textwidth
-  - \linespread{1.05}
-  - \usepackage{hyperref}
----
-
 ```{r setup, include=FALSE}
@@
 is_latex <- knitr::pandoc_to("latex")
+
+table_format <- ifelse(is_docx, "huxtable", 'default')
 
@@
 
-\vspace{.5cm}
-\begin{hypothesis}
-\begin{minipage}[t]{5.1 in}
-This is a hypothesis, but only for LaTeX.
+<!-- \vspace{.5cm} -->
+<!-- \begin{hypothesis} -->
+<!-- \begin{minipage}[t]{5.1 in} -->
+<!-- This is a hypothesis, but only for LaTeX.
 MS Word will pass over it like a good boy, as will HTML.
@@
 This will have to do.
-\end{minipage}
-\end{hypothesis}
-\vspace{.5cm}
+-->
+<!-- \end{minipage} -->
+<!-- \end{hypothesis} -->
+<!-- \vspace{.5cm} -->
 
@@
 Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence.
-Here's Table \@ref(tab:tab-reg).
 
-```{r tab-reg}
+```{r make-table}
 
@@
              align=c("lcc")) -> tab_reg
+```
 
-if (!is_docx) {
+```{r tab-reg-latex, eval=is_latex}
 tab_reg %>%
@@
   pack_rows("Stupid Thing I Added", 13, 14)
-} else {
+```
+
+```{r tab-reg-docx, eval=is_docx}
+# flextable would be nicer, but no real add_rows support here.
+# tab_reg %>%
+#   flextable::fontsize(size=10, part="all") %>%
+#   flextable::font(fontname = "Palatino", part="all") %>%
+#   flextable::padding(padding=1) %>%
+#   #flextable::add_body() %>%
+#   flextable::autofit()
+# #
+
 tab_reg %>%
@@
   as_flextable()
-} 
 ```
@@
 Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword.
-Here's Figure \@ref(fig:fig-sims).
 
-```{r fig-sims, fig.cap="Simulated Immigration Sentiment by Ideology"}
+```{r make-sims-ideology}
 
@@
   geom_pointrange() +
-  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)")
+  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims
 
+```
+
+```{r fig-sims-ideology-latex, eval=is_latex, fig.cap="Simulated Immigration Sentiment by Ideology"}
+fig_sims
+```
+
+```{r fig-sims-ideology-docx, eval=is_docx, fig.cap="Simulated Immigration Sentiment by Ideology", dev='png', dpi=600}
+fig_sims
 ```
@@
 # References
-
-<!-- This option seems to be more pleasing for rmarkdown::pdf_document() with my templates -->
-<!-- \setlength{\parskip}{6pt} -->
-
-<!-- If you're using bookdown, this seems to look better with bookdown::pdf_document2() -->
-\setlength{\parskip}{8pt}
-\setlength{\parindent}{-0.15in}
-\setlength{\leftskip}{0.15in}
-\vspace*{-0.35in}
-\noindent
-\singlespacing

### 2022-09-09 inst/skeleton/R/1-prep.R

@@ -1,28 +1,45 @@
-# load libraries ----
-# load the functions I need to process the data
-library(stevedata) # has the raw data
+prep <- function() {
+  set.seed(8675309)
+  ESS9GB %>%
+    mutate(noise = rnorm(nrow(.))) -> Data
 
-# "load" the data ----
-# Note: in your case, you can load raw data from wherever, even outside the project directory
-# For example, if you're analyzing ANES data, you're not ask to stick it in your project directory
-# If you can share the raw data, create a directory called "data-raw" in the main project directory
-# Then, load it from there.
-data(ESS9GB, package="stevedata")
+  saveRDS(Data, "data/Data.rds")
+  Data <<- Data
+  return(Data)
+}
 
-# "prep" the data ----
-# I can do anything I want here. I can recode things, transform variables, or whatever
-# Here, let's just create a stupid noise variable
 
-Data <- ESS9GB
+analysis <- function() {
+  Data <- readRDS("data/Data.rds")
+  Mods <- list()
+  Mods[[1]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale, data=Data)
+  Mods[[2]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale + noise, data=Data)
+  saveRDS(Mods, "data/Mods.rds")
+  Mods <<- Mods
+  return(Mods)
 
-set.seed(8675309)
-Data$noise <- rnorm(nrow(Data))
+}
 
-# in {tidyverse}
-# set.seed(8675309)
-# ESS9GB %>%
-#   mutate(noise = rnorm(nrow(.))) -> Data
+sims <- function() {
 
-# ^ Notice that I "finished" my data prep into a new object, titled "Data"
-# Now: I save it to data/Data.rds
-saveRDS(Data, "data/Data.rds")
+
+  Mods <- readRDS("data/Mods.rds")
+  Data <- readRDS("data/Data.rds")
+
+  Data %>%
+    data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
+              immigsent = 0) %>% na.omit -> newdat
+
+
+  Sims <- list()
+
+  newdat %>%
+    # repeat this data frame how many times we did simulations
+    dplyr::slice(rep(row_number(), 1000)) %>%
[…]

### 2022-09-09 inst/skeleton/R/2-analysis.R

@@ -1,8 +1,45 @@
-Data <- readRDS("data/Data.rds")
+prep <- function() {
+  set.seed(8675309)
+  ESS9GB %>%
+    mutate(noise = rnorm(nrow(.))) -> Data
 
-Mods <- list()
+  saveRDS(Data, "data/Data.rds")
+  Data <<- Data
+  return(Data)
+}
 
-Mods$"Default" <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale, data=Data)
-Mods$"Default + Noise" <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale + noise, data=Data)
 
-saveRDS(Mods, "data/Mods.rds")
+analysis <- function() {
+  Data <- readRDS("data/Data.rds")
+  Mods <- list()
+  Mods[[1]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale, data=Data)
+  Mods[[2]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale + noise, data=Data)
+  saveRDS(Mods, "data/Mods.rds")
+  Mods <<- Mods
+  return(Mods)
+
+}
+
+sims <- function() {
+
+
+  Mods <- readRDS("data/Mods.rds")
+  Data <- readRDS("data/Data.rds")
+
+  Data %>%
+    data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
+              immigsent = 0) %>% na.omit -> newdat
+
+
+  Sims <- list()
+
+  newdat %>%
+    # repeat this data frame how many times we did simulations
+    dplyr::slice(rep(row_number(), 1000)) %>%
+    bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
+
+
+  saveRDS(Sims, "data/Sims.rds")
+  Sims <<- Sims
+  return(Sims)
+}

### 2022-09-09 inst/skeleton/R/3-sims.R

@@ -1,32 +1,45 @@
-# Libraries first
-library(stevemisc)
-# library(tidyverse)
-library(modelr)
+prep <- function() {
+  set.seed(8675309)
+  ESS9GB %>%
+    mutate(noise = rnorm(nrow(.))) -> Data
 
-# Load stuff
-Mods <- readRDS("data/Mods.rds")
-Data <- readRDS("data/Data.rds")
-
-# in {tidyverse}
-# Data %>%
-#   data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
-#             immigsent = 0) %>% na.omit -> newdat
+  saveRDS(Data, "data/Data.rds")
+  Data <<- Data
+  return(Data)
+}
 
 
-Sims <- list()
+analysis <- function() {
+  Data <- readRDS("data/Data.rds")
+  Mods <- list()
+  Mods[[1]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale, data=Data)
+  Mods[[2]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale + noise, data=Data)
+  saveRDS(Mods, "data/Mods.rds")
+  Mods <<- Mods
+  return(Mods)
 
-na.omit(data_grid(Data, lrscale = unique(lrscale), .model = Mods[[1]], immigsent = 0)) -> newdat
+}
 
-Sims$"SQI (Ideology)" <- get_sims(Mods[[1]], newdat = newdat, 1000, 8675309)
-
-Sims[[1]]$lrscale <- rep(seq(0:10), 1000)
+sims <- function() {
 
 
+  Mods <- readRDS("data/Mods.rds")
+  Data <- readRDS("data/Data.rds")
 
-# in {tidyverse}
-# newdat %>%
-#   # repeat this data frame how many times we did simulations
-#   dplyr::slice(rep(row_number(), 1000)) %>%
-#   bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
+  Data %>%
+    data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
+              immigsent = 0) %>% na.omit -> newdat
 
-saveRDS(Sims, "data/Sims.rds")
+
+  Sims <- list()
+
+  newdat %>%
+    # repeat this data frame how many times we did simulations
[…]

### 2022-09-09 inst/skeleton/R/_render.R

@@ -1,0 +1,61 @@
+render_pdf <- function() {
+
+  ymlchars <- file.info("ms.yaml")$size
+  rmdchars <- file.info("ms.Rmd")$size
+
+  cat(paste0(readChar("ms.yaml",nchars=ymlchars),
+             readChar("ms.Rmd",nchars=rmdchars)),
+      file="tmp.Rmd")
+
+  the_output <- "latex"
+
+  rmarkdown::render("tmp.Rmd",
+                    output_file="doc/ms.pdf",
+                    bookdown::pdf_document2(template = stevetemplates::templ_article2(),
+                                            latex_engine = "xelatex", dev="cairo_pdf", toc = FALSE,
+                                            number_sections = FALSE))
+
+  delfiles <- dir(pattern="tmp|fff|log|ttt")
+  file.remove(delfiles)
+}
+
+render_pdfanon <- function() {
+
+  ymlchars <- file.info("ms.yaml")$size
+  rmdchars <- file.info("ms.Rmd")$size
+
+  cat(paste0(readChar("ms.yaml",nchars=ymlchars),
+             readChar("ms.Rmd",nchars=rmdchars)),
+      file="tmp.Rmd")
+
+  the_output <- "latex"
+
+  rmarkdown::render("tmp.Rmd",
+                    output_file="doc/ms-anon.pdf",
+                    params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
+                    bookdown::pdf_document2(template = stevetemplates::templ_article2(),
+                                            latex_engine = "xelatex", dev="cairo_pdf", toc = FALSE,
+                                            number_sections = FALSE))
+
+  delfiles <- dir(pattern="tmp|fff|log|ttt")
+  file.remove(delfiles)
+}
+
+
+render_docx <- function() {
+
+  ymlchars <- file.info("ms.yaml")$size
+  rmdchars <- file.info("ms.Rmd")$size
+
+  cat(paste0(readChar("ms.yaml",nchars=ymlchars),
+             readChar("ms.Rmd",nchars=rmdchars)),
+      file="tmp.Rmd")
+
+  the_output <- "word"
+
+  rmarkdown::render("tmp.Rmd", output_file="doc/ms.docx",
+                    rmarkdown::word_document(reference_docx = stevetemplates::templ_word()))
+
+  delfiles <- dir(pattern="tmp|fff|log|ttt")
+  file.remove(delfiles)
+}

### 2022-09-09 inst/skeleton/_targets.R

@@ -1,0 +1,29 @@
+library(targets)
+source("R/1-prep.R")
+source("R/2-analysis.R")
+source("R/3-sims.R")
+source("R/_render.R")
+tar_option_set(packages = c("stevedata", "tidyverse", "modelr", "stevemisc"))
+list(
+  tar_target(Data, prep()),
+  tar_target(Mods, {
+    Data
+    analysis()
+    }),
+  tar_target(Sims, {
+    Mods
+    Data
+    sims()
+  }),
+  tar_target(ms_rmd, "ms.Rmd", format = "file"),
+  tar_target(ms_yaml, "ms.yaml", format = "file"),
+  tar_target(docs, {Data
+    Mods
+    Sims
+    ms_rmd
+    ms_yaml
+    render_pdf()
+    render_pdfanon()
+    render_docx()
+    })
+)

### 2022-09-09 inst/skeleton/src/get_citations.R

@@ -1,53 +1,0 @@
-
-if_not_install <- function(packages) {
-  new_pack <- packages[!(packages %in% installed.packages()[,"Package"])]
-  if(length(new_pack)) install.packages(new_pack)
-}
-
-if_not_install(c("stringr", "dplyr", "magrittr",
-                 "rmarkdown", "bib2df"))
-
-
-library(stringr)
-library(dplyr)
-library(magrittr)
-library(rmarkdown)
-library(bib2df)
-
-doc <- readLines("ms.Rmd")
-the_entry <- yaml_front_matter("ms.Rmd")$bibliography
-
-read_bib <- function(x) {
-  if(str_starts(x, "`r ") == TRUE) {
-    ht <- str_remove_all(the_entry, "`")
-    ht <- str_remove(ht, "r ")
-
-    ht <- bib2df(eval(parse(text=ht)))
-    return(ht)
-  } else {
-    ht <- bib2df(the_entry)
-    return(ht)
-  }
-}
-
-the_bib <- read_bib(the_entry)
-
-
-cites <- c()
-
-for(i in 1:length(doc)) {
-  hold_this <- as.data.frame(str_match_all(doc[i], "@([[:alnum:]:&!~=_+-]+)")[[1]])
-  cites <- bind_rows(cites, hold_this)
-}
-
-cites %>% select(-V1) -> cites
-
-cites %>%
-  rename(BIBTEXKEY = V2) %>%
-  left_join(., the_bib) %>%
-  distinct(BIBTEXKEY, .keep_all = TRUE) %>%
-  # For now, this will tease out those wrong matches from the YAML or truly anything else
-  # It assumes, hopefully, you don't have a "gmail" entry in your .bib file or something to that effect
-  # In this application, that's where that's happening.
-  filter(!is.na(CATEGORY)) %>%
-  bib2df::df2bib(., file = "inst/refs.bib")

### 2022-09-09 inst/skeleton/src/render_abstract.R

@@ -1,32 +1,0 @@
-library(rmarkdown)
-library(ymlthis)
-library(magrittr)
-
-YAML <- yaml_front_matter("ms.Rmd")
-
-YAML[names(YAML) %in% c("title","author","abstract","keywords","geometry","mainfont")] %>%
-  as_yml() -> A
-
-A %>%
-  yml_rticles_opts(header_includes = "\\pagenumbering{gobble}") -> A
-
-yaml::write_yaml(A, file="doc/tmp.yml")
-
-cat(paste0("---\n",readr::read_file("doc/tmp.yml"), "\n---"), file="doc/tmp.Rmd")
-
-render("doc/tmp.Rmd",
-       output_file="abstract.pdf",
-       rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
-                               latex_engine = "xelatex", dev="cairo_pdf"))
-
-delfiles <- dir(path="doc/" ,pattern="tmp")
-file.remove(file.path("doc/", delfiles))
-
-# disabled for now...
-
-#tmp <- use_index_rmd(.yml = print(A), path='_dross', open_doc = FALSE)
-# render(tmp,
-#        output_file="abstract.pdf",
-#        rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
-#                                           latex_engine = "xelatex", dev="cairo_pdf"))
-# file.remove(tmp)

### 2022-09-09 inst/skeleton/src/render_docx.R

@@ -1,8 +1,0 @@
-# rmarkdown::render("ms.Rmd", output_file="doc/ms.docx", rmarkdown::word_document(reference_docx = stevetemplates::templ_word()))
-# ^ old, legacy, here if you want to revert to it.
-
-rmarkdown::render("ms.Rmd", output_file="doc/ms.docx",
-                  bookdown::word_document2(reference_docx = stevetemplates::templ_word(),
-                                           toc = FALSE, number_sections = FALSE))
-
-# ^ {bookdown} has table/figure cross-ref ability.

### 2022-09-09 inst/skeleton/src/render_html.R

@@ -1,4 +1,0 @@
-rmarkdown::render("ms.Rmd",
-                  output_file="doc/ms.html",
-                  bookdown::html_document2(template = stevetemplates::templ_html_article(),
-                                           toc = FALSE, number_sections = FALSE))

### 2022-09-09 inst/skeleton/src/render_pdf-anon.R

@@ -1,14 +1,0 @@
-# rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
-#                   params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
-#                   rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
-#                                           latex_engine = "xelatex", dev= "cairo_pdf"))
-# ^ old, legacy, here if you want to revert to it.
-
-
-rmarkdown::render("ms.Rmd", output_file="doc/ms-anon.pdf",
-                  params=list(anonymous=TRUE,doublespacing=TRUE,removetitleabstract=TRUE),
-                  bookdown::pdf_document2(template = stevetemplates::templ_article2(),
-                                          latex_engine = "xelatex", dev= "cairo_pdf",
-                                          toc = FALSE, number_sections = FALSE))
-
-# ^ {bookdown} has table/figure cross-ref ability.

### 2022-09-09 inst/skeleton/src/render_pdf.R

@@ -1,14 +1,0 @@
-# rmarkdown::render("ms.Rmd",
-#                   output_file="doc/ms.pdf",
-#                   rmarkdown::pdf_document(template = stevetemplates::templ_article2(),
-#                                           latex_engine = "xelatex", dev="cairo_pdf"))
-# ^ old, legacy, here if you want to revert to it.
-
-
-rmarkdown::render("ms.Rmd",
-                  output_file="doc/ms.pdf",
-                  bookdown::pdf_document2(template = stevetemplates::templ_article2(),
-                                          latex_engine = "xelatex", dev="cairo_pdf",
-                                          toc = FALSE, number_sections = FALSE))
-
-# ^ {bookdown} has table/figure cross-ref ability.

### 2022-09-09 inst/other_docs/appendix.Rmd
let me think on this a bit.

@@
 - name: Steven V. Miller
-  affiliation: Clemson University
-# thanks: "This is a work in progress. Feedback welcome: svmille@clemson.edu."
+  affiliation: Stockholm University
 # bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"

### 2022-09-10 inst/skeleton/R/_render.R
_config

@@ -1,9 +1,9 @@
 render_pdf <- function() {
 
-  ymlchars <- file.info("ms.yaml")$size
+  ymlchars <- file.info("_config.yaml")$size
   rmdchars <- file.info("ms.Rmd")$size
 
-  cat(paste0(readChar("ms.yaml",nchars=ymlchars),
+  cat(paste0(readChar("_config.yaml",nchars=ymlchars),
              readChar("ms.Rmd",nchars=rmdchars)),
       file="tmp.Rmd")
 
@@ -21,10 +21,10 @@ render_pdf <- function() {
 
 render_pdfanon <- function() {
 
-  ymlchars <- file.info("ms.yaml")$size
+  ymlchars <- file.info("_config.yaml")$size
   rmdchars <- file.info("ms.Rmd")$size
 
-  cat(paste0(readChar("ms.yaml",nchars=ymlchars),
+  cat(paste0(readChar("_config.yaml",nchars=ymlchars),
              readChar("ms.Rmd",nchars=rmdchars)),
       file="tmp.Rmd")
 
@@ -44,10 +44,10 @@ render_pdfanon <- function() {
 
 render_docx <- function() {
 
-  ymlchars <- file.info("ms.yaml")$size
+  ymlchars <- file.info("_config.yaml")$size
   rmdchars <- file.info("ms.Rmd")$size
 
-  cat(paste0(readChar("ms.yaml",nchars=ymlchars),
+  cat(paste0(readChar("_config.yaml",nchars=ymlchars),
              readChar("ms.Rmd",nchars=rmdchars)),
       file="tmp.Rmd")
 

### 2022-09-10 inst/other_docs/appendix.Rmd
change that, move to a central _config.yaml

@@
----
-title: "APPENDIX: [Insert Paper Title Here]"
-author:
-- name: Carl Sagan
-  affiliation: Cornell University & the Cosmos
-- name: Steven V. Miller
-  affiliation: Stockholm University
-# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"
-# biblio-style: apsr
-geometry: margin=1in
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-fontsize: 11pt
-keywords: ""
-endnotes: FALSE
-# csl: inst/jpr.csl
-mainfont: cochineal
-# sansfont: Linux Biolinum O
-sansitup: FALSE
-params:
-  anonymous: ""
-  doublespacing: ""
-  removetitleabstract: ""
-appendix: TRUE
-appendixletter: "A"
-pandocparas: FALSE
-anonymous: "`r params$anonymous`"
-doublespacing: "`r params$doublespacing`"
-removetitleabstract: "`r params$removetitleabstract`"
-linkcolor: black
-header-includes:
-  - \usepackage{longtable}
-  - \usepackage{csquotes}
-  - \LTcapwidth=.95\textwidth
-  - \linespread{1.05}
-  - \usepackage{hyperref}
-  - \usepackage{setspace}
-  - \renewcommand{\thepage}{A-\arabic{page}}
----
-
+<!-- APPENDIX -->
 ```{r setup, include=FALSE}

### 2022-09-12 inst/skeleton/R/1-prep.R
futz

@@ -7,39 +7,3 @@ prep <- function() {
   Data <<- Data
   return(Data)
 }
-
-
-analysis <- function() {
-  Data <- readRDS("data/Data.rds")
-  Mods <- list()
-  Mods[[1]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale, data=Data)
-  Mods[[2]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale + noise, data=Data)
-  saveRDS(Mods, "data/Mods.rds")
-  Mods <<- Mods
-  return(Mods)
-
-}
-
-sims <- function() {
-
-
-  Mods <- readRDS("data/Mods.rds")
-  Data <- readRDS("data/Data.rds")
-
-  Data %>%
-    data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
-              immigsent = 0) %>% na.omit -> newdat
-
-
-  Sims <- list()
-
-  newdat %>%
-    # repeat this data frame how many times we did simulations
-    dplyr::slice(rep(row_number(), 1000)) %>%
-    bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
-
-
-  saveRDS(Sims, "data/Sims.rds")
-  Sims <<- Sims
-  return(Sims)
-}

### 2022-09-12 inst/skeleton/R/2-analysis.R

@@ -1,14 +1,3 @@
-prep <- function() {
-  set.seed(8675309)
-  ESS9GB %>%
-    mutate(noise = rnorm(nrow(.))) -> Data
-
-  saveRDS(Data, "data/Data.rds")
-  Data <<- Data
-  return(Data)
-}
-
-
 analysis <- function() {
   Data <- readRDS("data/Data.rds")
   Mods <- list()
@@ -18,28 +7,4 @@ analysis <- function() {
   Mods <<- Mods
   return(Mods)
 
-}
-
-sims <- function() {
-
-
-  Mods <- readRDS("data/Mods.rds")
-  Data <- readRDS("data/Data.rds")
-
-  Data %>%
-    data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
-              immigsent = 0) %>% na.omit -> newdat
-
-
-  Sims <- list()
-
-  newdat %>%
-    # repeat this data frame how many times we did simulations
-    dplyr::slice(rep(row_number(), 1000)) %>%
-    bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
-
-
-  saveRDS(Sims, "data/Sims.rds")
-  Sims <<- Sims
-  return(Sims)
 }

### 2022-09-12 inst/skeleton/R/3-qis.R

@@ -1,0 +1,23 @@
+qi <- function() {
+
+
+  Mods <- readRDS("data/Mods.rds")
+  Data <- readRDS("data/Data.rds")
+
+  Data %>%
+    data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
+              immigsent = 0) %>% na.omit -> newdat
+
+
+  QI <- list()
+
+  newdat %>%
+    # repeat this data frame how many times we did simulations
+    dplyr::slice(rep(row_number(), 1000)) %>%
+    bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> QI$"SQI (Ideology)"
+
+
+  saveRDS(QI, "data/QI.rds")
+  QI <<- QI
+  return(QI)
+}

### 2022-09-12 inst/skeleton/R/3-sims.R

@@ -1,45 +1,0 @@
-prep <- function() {
-  set.seed(8675309)
-  ESS9GB %>%
-    mutate(noise = rnorm(nrow(.))) -> Data
-
-  saveRDS(Data, "data/Data.rds")
-  Data <<- Data
-  return(Data)
-}
-
-
-analysis <- function() {
-  Data <- readRDS("data/Data.rds")
-  Mods <- list()
-  Mods[[1]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale, data=Data)
-  Mods[[2]] <- lm(immigsent ~ agea + female + eduyrs + uempla + hinctnta + lrscale + noise, data=Data)
-  saveRDS(Mods, "data/Mods.rds")
-  Mods <<- Mods
-  return(Mods)
-
-}
-
-sims <- function() {
-
-
-  Mods <- readRDS("data/Mods.rds")
-  Data <- readRDS("data/Data.rds")
-
-  Data %>%
-    data_grid(lrscale = unique(lrscale), .model = Mods[[1]],
-              immigsent = 0) %>% na.omit -> newdat
-
-
-  Sims <- list()
-
-  newdat %>%
-    # repeat this data frame how many times we did simulations
-    dplyr::slice(rep(row_number(), 1000)) %>%
-    bind_cols(get_sims(Mods[[1]], newdata = newdat, 1000, 8675309), .) -> Sims$"SQI (Ideology)"
-
-
-  saveRDS(Sims, "data/Sims.rds")
-  Sims <<- Sims
-  return(Sims)
-}

### 2022-09-12 inst/skeleton/ms.Rmd
more cosmetic changes

@@
 
-Sims[[1]] %>% 
+QI[[1]] %>% 
   group_by(lrscale) %>% 

### 2022-09-12 inst/skeleton/_targets.R

@@ -1,7 +1,7 @@
 library(targets)
 source("R/1-prep.R")
 source("R/2-analysis.R")
-source("R/3-sims.R")
+source("R/3-qi.R")
 source("R/_render.R")
 tar_option_set(packages = c("stevedata", "tidyverse", "modelr", "stevemisc"))
 list(
@@ -10,16 +10,16 @@ list(
     Data
     analysis()
     }),
-  tar_target(Sims, {
+  tar_target(QI, {
     Mods
     Data
-    sims()
+    qi()
   }),
   tar_target(ms_rmd, "ms.Rmd", format = "file"),
-  tar_target(ms_yaml, "ms.yaml", format = "file"),
+  tar_target(ms_yaml, "_config.yaml", format = "file"),
   tar_target(docs, {Data
     Mods
-    Sims
+    QI
     ms_rmd
     ms_yaml
     render_pdf()
